### 2022-03-04 paper-kelompok/main.tex
inisialisasi paper kelompok

\documentclass[conference]{IEEEtran}
\usepackage{cite}

\title{UV-VIS Spectrophometer berbasis single beam}
\author{\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
\textit{Institut Teknologi Bandung}\\
Bandung, Indonesia\\
Email:}}

% ganti abstract menjadi absktrak
\renewcommand{\abstractname}{Abstrak}

% ganti index term menjadi Kata Kunci
\renewcommand{\IEEEkeywordsname}{Kata Kunci}

\begin{document}

% ini komentar
\maketitle

\begin{abstract}
    Instrumen yang telah dikembangkan kelompok Tugas Akhir Teknik Elektro sebelumnya adalah sebuah spektrofotometer portabel yang dapat bekerja pada spektrum gelombang ultraviolet dan cahaya tampak, atau umumnya disebut spektrofotometer UV-Vis. Spektrofotometer yang dibuat hanya dapat melakukan perhitungan intensitas cahaya secara relatif terhadap nilai intensitas tertinggi yang terukur, tidak dilakukan kalibrasi skala panjang gelombang dan tuning fungsi konversi citra. Hal ini menunjukkan bahwa pengukuran yang dilakukan masih bersifat kualitatif. Spektrofotometer yang telah dikembangkan kelompok Tugas Akhir Teknik Elektro belum memiliki kapabilitas untuk 
\end{abstract}

\begin{IEEEkeywords}
    UV-VIS Spectrophotometry
\end{IEEEkeywords}

% Pendahuluan
\section{Pendahuluan}
ini dalah pendahuluan

% Pendahuluan
\section{Pekerjaan Terkait}
ini dalah pendahulua~c\cite{gutierrez2012dispersion}

% Pendahuluan
\section{Desain Sistem}
ini dalah pendahuluan

% Pendahuluan
\section{Hasil dan Pembasahan}
ini dalah pendahuluan

% Pendahuluan
\section{Kesimpulan}
ini dalah pendahuluan

% Referensi
\bibliographystyle{IEEEtran}
\bibliography{referensi.bib}

\end{document}

### 2022-10-05 paper-kelompok/main.tex
copy from ms words

@@
 \usepackage{cite}
-
-\title{UV-VIS Spectrophometer berbasis single beam}
-\author{\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
-\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-\textit{Institut Teknologi Bandung}\\
-Bandung, Indonesia\\
-Email:}}
-
-% ganti abstract menjadi absktrak
-\renewcommand{\abstractname}{Abstrak}
-
-% ganti index term menjadi Kata Kunci
-\renewcommand{\IEEEkeywordsname}{Kata Kunci}
-
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
 
-% ini komentar
+\title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}
+
+\author{\IEEEauthorblockN{Alzana Armaniar Farhani}
+\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\textit{and Informatics} \\
+\textit{Institut Teknologi Bandung}\\
+Bandung, Indonesia \\
+Email: farhanialzana@gmail.com}
+\and
+\IEEEauthorblockN{Balkan Khilmi Assakandari}
+\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\textit{and Informatics} \\
+\textit{Institut Teknologi Bandung}\\
+Bandung, Indonesia \\
+Email: balkankhilmi@gmail.com}
+\and
+\IEEEauthorblockN{Anindhita Nayazirly}
+\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\textit{and Informatics} \\
+\textit{Institut Teknologi Bandung}\\
+Bandung, Indonesia \\
+Email: zirlysukarno@gmail.com}
+\and
+\IEEEauthorblockN{Akhmadi Surawijaya}
+\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
+\textit{Institut Teknologi Bandung}\\
+Bandung, Indonesia \\
+Email:}
+\and
+\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
+\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
+\textit{Institut Teknologi Bandung}\\
+Bandung, Indonesia \\
+Email:}
+}
+
 \maketitle
+
+% \title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}
+
+% \author{\IEEEauthorblockN{Alzana Armaniar Farhani}
+% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
+% \textit{Institut Teknologi Bandung}\\
+% Bandung, Indonesia\\
+% Email: farhanialzana@gmail.com}
+% \and
+% \IEEEauthorblockN{Balkan Khilmi Assakandari}
+% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
+% \textit{Institut Teknologi Bandung}\\
+% Bandung, Indonesia\\
+% Email: balkankhilmi@gmail.com}
+% \and
+% \IEEEauthorblockN{Anindhita Nayazirly}
+% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
+% \textit{Institut Teknologi Bandung}\\
+% Bandung, Indonesia\\
+% Email: zirlysukarno@gmail.com}
+% \and
+% \IEEEauthorblockN{Akhmadi Surawijaya}
+% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
+% \textit{Institut Teknologi Bandung}\\
+% Bandung, Indonesia\\
+% Email: }
+% \and
+% \IEEEauthorblockN{Muhammad Ogin Hasanuddin}
+% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
+% \textit{Institut Teknologi Bandung}\\
+% Bandung, Indonesia\\
+% Email: }}
+
+% % ini komentar
+% \maketitle
 
@@
 % Pendahuluan
-\section{Pendahuluan}
-ini dalah pendahuluan
+\section{Introduction}
+Currently, various methods detect and measure glucose concentrations in food matrices.
+These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic instrumentation, such as HPLC systems.
+While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well.
+However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
+Spectrophotometric tests utilize the light transmitted or reflected by a sample to perform qualitative and quantitative analysis.
+For qualitative analysis, the light transmitted by a sample has a unique spectrum based on the atoms or molecules contained in the sample.
+
+Meanwhile, for quantitative analysis, the absorbance level of the sample for a specific wavelength is directly proportional to the concentration of the sample.
+Glucose spectrophotometry test includes colorimetric measurement methods, namely measurements that involve changing the color of the sample to measure quantities such as absorbance and sample concentration.
+Various colorimetric methods involving reactions with different enzymes for glucose measurement are the object of research being developed to obtain colorimetric methods that are accurate, sensitive, selective, and inexpensive.
+Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H2O2).
+In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors[1].
+
+Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means.
+One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems.
+The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric[2].
+The DMF system mainly consists of a fluid layer located between the top and bottom plates.
+Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics[3].
+Droplet mixing allows all chemical reactions to be done on chip.
+An optical detection system needs to be developed in order to measure the absorbance and concentration of a glucose droplet on the DMF chip.
+
+In this study, we present the development of a portable visible spectrophotometer, which is detachable to DMF platforms.
+It allows the integration with a DMF platform and can be removed if the DMF is needed for other purposes.
+A light will be emitted through the droplet located on the DMF chip and an array of photodetectors will collect the intensity of incident light.
+A program is uploaded to the system to compute the absorbance and the concentration of the sample droplet.
+Users can interact with the system using four input buttons and an LCD which displays the result of the measurements.
+
+The current version of the spectrophotometer has some features as follows:
+\begin{itemize}
+    \item Concentration measurement of microdroplet samples 
+    \item Absorbance measurement of samples based on wavelength characteristic 
+    \item Able to work in visible spectrum (400 nm to 700 nm) 
+    \item Able to be integrated with a digital microfluidic platform 
+    \item The measurement results can be displayed on an LCD and stored 
+    \item Portable (12cm x 13cm x 20cm)
+\end{itemize}
+
+\section{Methods}
+\subsection{System Overview}
+The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem.
+Its data flow diagram (DFD) can be seen in Fig.
+1.
+The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector.
+The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform.
+The light which is not absorbed by the droplet will pass through the slit then to a monochromator.
+The monochromator decomposes the light into monochromatic light to be detected by the photodetector array.
+Each detector in the array measures the light intensity for a specific wavelength.
+The measurement readings will be sent to the control subsystem to be computed into absorbance values.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{system-dfd.png}}
+    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
+    \label{system-dfd}
+    \end{figure}
+
+\subsection{Light Source Subsystem}
+The light source subsystem functions to produce polychromatic light as the primary variable to be manipulated and measured by the instrument.
+This subsystem includes 2 modules, namely switching circuits and light sources.
+The process in this subsystem begins with receiving a control signal from the control subsystem to the switching circuit.
+The switching circuit then flows the source voltage to the lamp so that it can be lit.
+The polychromatic light source will illuminate and produce light with all UV-Vis frequencies within the specification.
+This light is then passed on to the sample for a certain period.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{light-source-dfd.png}}
+    \caption{DFD of the light source subsystem.}
+    \label{light-source-dfd}
+    \end{figure}
+
+\subsection{Light Sensor Subsystem}
+The light sensor subsystem functions as a spectrometer that receives polychromatic light beam and outputs light intensities of discrete wavelengths in the form of digital data.
+Polychromatic light beam enters the sensor subsystem through a hole and gets diffracted by a transmissive diffraction grating as to spatially separate light by its wavelengths.
+The grating has a groove density of 1200 lines per millimeter, thus only the first order of diffraction is usable to separate the visible spectrum.
+The resulting ray is then recorded by Micron® Imaging MT9M001 Monochrome CMOS digital image sensor.
+Different pixel of the image sensor captures the intensity of different wavelengths ranging from 400 nanometer to 700 nanometer formatted into 10-bit unsigned integer.
+The light sensor subsystem outputs, at maximum, 1280 16-bit unsigned integer values, each value representing the light intensity of certain wavelengths.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{light-sensor-dfd.png}}
+    \caption{DFD of the light sensor subsystem.}
+    \label{light-sensor-dfd}
+    \end{figure}
+
+\subsection{Control Subsystem}
+The subsystems in the spectrophotometer are controlled by a ESP32-S3-WROOM-1-N8 microcontroller module (Espressif Systems, Shanghai, China).
+The task of the control subsystem is to execute the main workflow of the spectrophotometer by a FSM.
+The control subsystem synchronizes other subsystems, such as the light source with the light sensor when measuring light intensities.
+The subsystem also has non-volatile memory storage to save past absorbance measurements and concentration calibration curves.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{control-dfd.png}}
+    \caption{DFD of the control subsystem.}
+    \label{control-dfd}
+    \end{figure}
+
+\subsection{User Interface Subsystem}
+The user interface subsystem plays a role in connecting the system and the users.
+This can be done by interpreting the commands given by users through the input interface devices and process it into control signals that will be sent to the control subsystem.
+The subsystem also has a function to display measurement data which include sample concentration values, sample absorbance spectrum, regression curves, menus, and settings.
+Fig.
+5 shows the data flow diagram of the user interface subsystem.
+
+Four push buttons and a power switch are used as the input interface devices.
+For the display, a 3.5-inch non-touchscreen TFT LCD with ILI9488 driver is used.
+The configuration of buttons and non-touchscreen LCD is chosen because it fits the users who use the spectrophotometer using laboratory gloves.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{ui-dfd.png}}
+    \caption{DFD of the user interface subsystem.}
+    \label{ui-dfd}
+    \end{figure}
+
+\subsection{Power Subsystem}
+The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit.
+The battery can be recharged easily whenever the battery voltage is insufficient.
+The power subsystem also provides information about the battery voltage value to be displayed to the user.
+
+The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller.
+The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold.
+If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics{power-dfd.png}}
+    \caption{DFD of the power subsystem.}
+    \label{power-dfd}
+    \end{figure}
 
 % Pendahuluan
-\section{Pekerjaan Terkait}
-ini dalah pendahulua~c\cite{gutierrez2012dispersion}
+\section{Results and Discussion}
+\subsection{Accuracy}
+\subsection{Repeatability}
+\subsection{Wavelength Range}
+\subsection{Device and DMF Cartridge Distance}
+\subsection{Electronic Display Size}
+\subsection{Weight and Size}
 
-% Pendahuluan
-\section{Desain Sistem}
-ini dalah pendahuluan
+\section{Conclusions}
 
-% Pendahuluan
-\section{Hasil dan Pembasahan}
-ini dalah pendahuluan
+\section*{References}
 
-% Pendahuluan
-\section{Kesimpulan}
-ini dalah pendahuluan
-
-% Referensi
-\bibliographystyle{IEEEtran}
-\bibliography{referensi.bib}
+\begin{thebibliography}{00}
+\bibitem{b1} H.
+V.
+Tran et al., “Silver nanoparticles-decorated reduced graphene oxide: A novel peroxidase-like activity nanomaterial for development of a colorimetric glucose biosensor,” Arabian Journal of Chemistry, vol.
+13, no.
+7, pp.
+6084–6091, Jul.
+2020, doi: 10.1016/j.arabjc.2020.05.008.
+\bibitem{b2} Z.
+Gu, M.
+L.
+Wu, B.
+Y.
+Yan, H.
+F.
+Wang, and C.
+Kong, “Integrated Digital Microfluidic Platform for Colorimetric Sensing of Nitrite,” ACS Omega, vol.
+5, no.
+19, pp.
+11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
+\bibitem{b3} S.
+Huang and R.
+B.
+Fair, “Quantitative measurements of inorganic analytes on a digital microfluidics platform,” SN Applied Sciences, vol.
+1, no.
+12, Dec.
+2019, doi: 10.1007/s42452-019-1693-8.
+\end{thebibliography}
 

### 2022-10-05 paper-kelompok/main.tex
delete comments
figure scaling
connect citing

@@
 
-% \title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}
-
-% \author{\IEEEauthorblockN{Alzana Armaniar Farhani}
-% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-% \textit{Institut Teknologi Bandung}\\
-% Bandung, Indonesia\\
-% Email: farhanialzana@gmail.com}
-% \and
-% \IEEEauthorblockN{Balkan Khilmi Assakandari}
-% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-% \textit{Institut Teknologi Bandung}\\
-% Bandung, Indonesia\\
-% Email: balkankhilmi@gmail.com}
-% \and
-% \IEEEauthorblockN{Anindhita Nayazirly}
-% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-% \textit{Institut Teknologi Bandung}\\
-% Bandung, Indonesia\\
-% Email: zirlysukarno@gmail.com}
-% \and
-% \IEEEauthorblockN{Akhmadi Surawijaya}
-% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-% \textit{Institut Teknologi Bandung}\\
-% Bandung, Indonesia\\
-% Email: }
-% \and
-% \IEEEauthorblockN{Muhammad Ogin Hasanuddin}
-% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
-% \textit{Institut Teknologi Bandung}\\
-% Bandung, Indonesia\\
-% Email: }}
-
-% % ini komentar
-% \maketitle
-
 \begin{abstract}
@@
 Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H2O2).
-In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors[1].
+In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b1}.
 
@@
 One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems.
-The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric[2].
+The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b2}.
 The DMF system mainly consists of a fluid layer located between the top and bottom plates.
-Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics[3].
+Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b3}.
 Droplet mixing allows all chemical reactions to be done on chip.
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{system-dfd.png}}
+    \centerline{\includegraphics[scale=0.4]{system-dfd.png}}
     \caption{Level-1 Data Flow Diagram (DFD) of the system.}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{light-source-dfd.png}}
+    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
     \caption{DFD of the light source subsystem.}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{light-sensor-dfd.png}}
+    \centerline{\includegraphics[scale=0.4]{light-sensor-dfd.png}}
     \caption{DFD of the light sensor subsystem.}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{ui-dfd.png}}
+    \centerline{\includegraphics[scale=0.4]{ui-dfd.png}}
     \caption{DFD of the user interface subsystem.}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{power-dfd.png}}
+    \centerline{\includegraphics[scale=0.6]{power-dfd.png}}
     \caption{DFD of the power subsystem.}

### 2022-11-02 paper-kelompok/main.tex
figure refrencing
author block formatting and sensor dfd

@@
 
+\makeatletter
+\newcommand{\newlineauthors}{%
+  \end{@IEEEauthorhalign}\hfill\mbox{}\par
+  \mbox{}\hfill\begin{@IEEEauthorhalign}
+}
+\makeatother
+
 \title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}
@@
 \author{\IEEEauthorblockN{Alzana Armaniar Farhani}
-\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
+\textit{School of Electrical Engineering} \\
 \textit{and Informatics} \\
@@
 Bandung, Indonesia \\
-Email: farhanialzana@gmail.com}
+farhanialzana@gmail.com}
 \and
 \IEEEauthorblockN{Balkan Khilmi Assakandari}
-\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
+\textit{School of Electrical Engineering} \\
 \textit{and Informatics} \\
@@
 Bandung, Indonesia \\
-Email: balkankhilmi@gmail.com}
+balkankhilmi@gmail.com}
 \and
 \IEEEauthorblockN{Anindhita Nayazirly}
-\IEEEauthorblockA{\textit{School of Electrical Engineering} \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
+\textit{School of Electrical Engineering} \\
 \textit{and Informatics} \\
@@
 Bandung, Indonesia \\
-Email: zirlysukarno@gmail.com}
-\and
+zirlysukarno@gmail.com}
+\newlineauthors
 \IEEEauthorblockN{Akhmadi Surawijaya}
-\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
+\textit{School of Electrical Engineering} \\
+\textit{and Informatics} \\
 \textit{Institut Teknologi Bandung}\\
 Bandung, Indonesia \\
-Email:}
+email}
 \and
 \IEEEauthorblockN{Muhammad Ogin Hasanuddin}
-\IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics} \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
+\textit{School of Electrical Engineering} \\
+\textit{and Informatics} \\
 \textit{Institut Teknologi Bandung}\\
 Bandung, Indonesia \\
-Email:}
+email}
 }
@@
 The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem.
-Its data flow diagram (DFD) can be seen in Fig.
-1.
+Its data flow diagram (DFD) is shown in Fig.
+\ref{system-dfd}.
 The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector.
@@
 Polychromatic light beam enters the sensor subsystem through a hole and gets diffracted by a transmissive diffraction grating as to spatially separate light by its wavelengths.
-The grating has a groove density of 1200 lines per millimeter, thus only the first order of diffraction is usable to separate the visible spectrum.
-The resulting ray is then recorded by Micron® Imaging MT9M001 Monochrome CMOS digital image sensor.
+The grating has a groove density of 1200 lines/mm, and the first order of diffraction is used to separate the visible spectrum.
+The resulting ray is then recorded by a CMOS image sensor (Arducam MT9M001 Monochrome Camera Module).
 Different pixel of the image sensor captures the intensity of different wavelengths ranging from 400 nanometer to 700 nanometer formatted into 10-bit unsigned integer.
-The light sensor subsystem outputs, at maximum, 1280 16-bit unsigned integer values, each value representing the light intensity of certain wavelengths.
+The light sensor subsystem outputs, at maximum, 400 16-bit unsigned integer values, each value representing the light intensity of wavelengths in the visible spectrum range.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.4]{light-sensor-dfd.png}}
+    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
     \caption{DFD of the light sensor subsystem.}
@@
 Fig.
-5 shows the data flow diagram of the user interface subsystem.
+\ref{ui-dfd} shows the data flow diagram of the user interface subsystem.
 
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.4]{ui-dfd.png}}
+    \centerline{\includegraphics[scale=0.43]{ui-dfd.png}}
     \caption{DFD of the user interface subsystem.}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{power-dfd.png}}
+    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
     \caption{DFD of the power subsystem.}

### 2022-11-30 HardwareX - Spectrophotometer/main.tex
penambahan template hardwareX

% GENERAL INFORMATION: HardwareX is an open access journal established to promote free and open source designing, building and customizing of scientific infrastructure (hardware). For more details on best practices for sharing open hardware see http://www.oshwa.org/sharing-best-practices/

\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{tabu}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{svg}
\usepackage{subcaption}
\newlist{selectlist}{itemize}{2}
\setlist[selectlist]{label=$\square$,leftmargin=*,noitemsep,topsep=0pt}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
% \hypersetup{
%      colorlinks=true,
%      linkcolor=black,
%      filecolor=magenta,      
%      urlcolor=black,
% }

\urlstyle{same}

% Set up the section label formatting
\titleformat{\section}[block]{\hspace{1em}\bfseries}{\thesection.}{0.5em}{} 
\titleformat{\subsection}[block]{\hspace{1em}}{\thesubsection}{0.5em}{}

% setup untuk memisahkan per section-nya jadi file .tex\
\usepackage{subfiles}

% setup sitasi
\usepackage{cite}
%\addbibresource{references.bib}

% memulai dokumen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Create the title block
\begin{flushleft}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
% \textbf{\large HardwareX article template}

%Insert title
%Max. 20 words. A good title should contain the fewest possible words that adequately describe the content of a paper.
\textbf{Title:} SpectroDMF: An Open Source Portable Visible Spectrophotometer for Microdroplet Measurements in Digital Microfluidics

%Insert Authors
\textbf{Authors:} Akhmadi Surawijaya$^1$, Muhammad Ogin Hasanuddin$^2$, Alzana Armaniar Farhani, Balkan Khilmi Assakandari, and Anindhita Nayazirly

%Insert Affiliations
\textbf{Affiliations:}\\
School of Electrical Engineering and Informatics, Institut Teknologi Bandung, Bandung, Indonesia;

%Insert Contact Email
%Include institutional email address of the corresponding author
\textbf{Contact email:} $^1$moginh@staff.stei.itb.ac.id, $^2$moginh@itb.ac.id

%Insert Abstract
%Max. 200 words. Remember that the abstract is what readers see first in electronic abstracting and indexing services. This is the advertisement of your article. Make it interesting, and easy to be understood. Be accurate and specific, keep it as brief as possible.
\textbf{Abstract:} Hippotherapy is one of the highly effective treatment methods for Cerebral Palsy (CP) rehabilitation by using horse riding activity, which is beneficial to the patient because the stimuli: horse gait which is very similar to mechanical gait in humans and also visual input from the environment. However, the need of large area, quiet environment, and high maintenance costs of the facilities lead to expensive treatment. To solve this problem, we use a store-bought horse riding simulator device, and also give visual input through a simple game and an immersive virtual environment. The device then can be put in a room in a hospital for the patient's therapy. A therapy in hospital is covered by the Indonesian healthcare, thus affordable an beneficial, especially for children with CP families with low-income socioeconomic condition. This article provides the design of the system, block diagrams, game design, build instructions, and software codes needed for building the device.

%Insert Keywords
% At least 3 keywords. There is no limit on the no. of keywords you can list. Please remember that effective keywords should not repeat words appearing in your title, and should be neither too general nor too narrow.
\textbf{Keywords:} UV-VIS Spectrophotometry

\input{sec0_spec}
% create the main body of the paper
\newpage
\input{sec1_hwic}
\input{sec2_hwdesc}
\input{sec3_designfiles}
\input{sec4_bom}
\input{sec5_buildinstr}
\input{sec6_operation}
\input{sec7_validation}
% \input{sec8_acknow}
\input{sec9_interest}
\input{sec10_rights}
\end{flushleft}

\section*{References} 
%> Include at least one reference, to the original publication of the hardware you customized.
%> Include other references as required. Include references to put your device in context in the literature. For more information on the reference format in HardwareX please see the Guide for Authors at: https://www.elsevier.com/journals/hardwarex/2468-0672/guide-for-authors

\textit{\begin{itemize}
\item Include at least one reference, to the original publication of the hardware you customized.
\item Include other references as required. Include references to put your device in context in the literature. For more information on the reference format in HardwareX please see the Guide for Authors at: https://www.elsevier.com/journals/hardwarex/2468-0672/guide-for-authors
\end{itemize}}

% menampilkan referensi %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\printbibliography
\bibliographystyle{ieeetr}
\bibliography{references}

\end{document}

%> Author manuscript checklist
%> ●	HardwareX is a journal dedicated to the exhaustive and fully open source communication of advances in scientific infrastructure. Upon submission the author declares that all information necessary to reproduce the subject of the submission (e.g. bill of materials, build instructions, calibration procedures, source files, code, and safety considerations) is communicated in full and is accessible for use under an open source license. 
%> ●	Is the subject of the submission under an open source license? Are design files in the preferred format for making modifications? As defined by the Open Source Hardware definition. 
%> ●	Can the hardware be reproduced with the details provided in the submission?
%> ●	Are all relevant design files available on Mendeley Data, the Open Science Framework, or Zenodo repositories, described in the Summary of Design Files document, and clearly documented? (e.g. descriptive file names, commented code, labeled images, etc.) 
%>      ○	If in the Open Science Framework, the repository has be registered? Instructions
%>      ○	If in Zenodo, the repository is open access and is published? Instructions
%>      ○	If in Mendeley Data, the repository is published or the sharable link was included in the additional information of the Editorial Submission interface? Instructions
%> ●	Are visual instructions used when necessary?
%> ●	Is the utility of the hardware to the scientific community? Has a specific scientific application been demonstrated using the hardware?
%> ●	Is the performance of the hardware adequately demonstrated and characterized?
%> ●	Are all potential safety concerns addressed?
%> ●	For more information on the article template consult the Guide to Authors.}

### 2022-11-30 HardwareX - Spectrophotometer/sec1_hwic.tex
penambahan template hardwareX

\section{Hardware in context}
% masih copas dari paper dome

% Cerebral palsy (CP) refers to a group of permanent motor disorders attributed to a non-progressive lesion in the immature brain \cite{Rosenbaum2007A2006}. Children with CP may have a limitation or impairment in their movements, which may disrupt their daily activities \cite{Beckung2007TheYears,Wright2008HowPalsy}.

\textcolor{red}{Hippotherapy is one of the Cerebral Palsy (CP) rehabilitation methods using a horse's movements characteristics to provide motor and sensory input to the patients \cite{Koca2015WhatHippotherapy}.
A number researchers report positive results on randomized controlled trials and a studies of hippotherapy to support the method's effectiveness.
Improving motor function, symmetry of muscle contraction, spasticity, posture, and walking is the benefit gained from hippotherapy \cite{Pantera2022DoesFunctioning}.}

\textcolor{red}{However, hippotherapy activities are costly and challenging to conduct due to several factors. The therapy instructor has to have a horse riding instructor license and therapist qualification. They also must be able to prepare the horse and guide the patients in a session. Finding a therapist with the skill mentioned earlier is challenging in a developing country like Indonesia.
Aside from human resource costs, horse-keeping requires massive land use for a ranch or farm, which is expensive and impossible to do in urban environments \cite{Scott2005SpecialRiding}.
Currently, no place offers a hippotherapy session with real horses in Indonesia. The last activity reported about hippotherapy sessions in Indonesia was in 2009 \cite{Setyawan2010TerapiAutisme}, making access to real-horse hippotherapy unavailable for children with CP in Indonesia.}

% solving the cost with horse riding simulator. Cite HRS simulators.
\textcolor{red}{Some researchers suggest using a Horse Riding Simulator (HRS) instead of using actual horses because it can significantly reducing the cost of hippotherapy. An HRS device is commonly available in the market as an exercise or fitness machine.
% cite this: hippotherapy using simulator.
Many recent researches \cite{Temcharoensuk2015EffectTrial,Dominguez-Romero2019EffectivenessMeta-Analysis, Kim2018EquineRiding, Chinniah2020EffectsPalsy} reported that HRS usage also shows positive results for CP treatments similar to hippotherapy with a real horse.
% what problem solved by simulator
Using a simulator, we only need a room with all the required equipment, eliminating the need for large horse farms in rural areas. However, this setup also has several drawbacks. Children are quickly bored doing monotonous and repetitive actions in a room without fun stimuli. The room setup also loses visual stimulation from the outside environment, which usually helps motivate the children to finish the therapy session and return to the next session.}

% exergaming design motivations
\textcolor{red}{Providing fun content to the children is essential to prevent the lack of enthusiasm of the children. One of the fun activities is \textit{exergaming} or active video gaming that requires bodily movements to play \cite{Benzing2018ExergamingThreats}. 
% benefits of exergaming.
Exergaming also benefits children with CP by improving muscle strength \cite{Viana2021TheMeta-analysis}, balance \cite{Meyns2021ExergamingTrial}, range of motion \cite{Chen2007UseDesign}, and physical fitness \cite{Widman2006EffectivenessDysfunction} depending on the type of body movements required to control the game.
% our design to exergaming
In this report, we design an exergaming video game to solve the problem mentioned earlier in the form of a horse racing-like game with tasks to pick apples and avoiding obstacles. We name the game \textit{Sirkus Apel}, which means "apple circus" in Indonesian. We also develop a controller that requires the user to move their back to control the in-game horse. A case report shows that back exercises also benefit children with CP, with the subject showing excellent motor progression \cite{Novak2016PromotingReport}.}

% Virtual reality motivations
\textcolor{red}{A room setup also removes the refreshing view of a horse ranch which provides visual stimulation to the children. This problem motivates us to design the game in an immersive virtual reality (VR) environment to enhance the exergaming experience.
% Problem with the usual VR
However, considering the safety of the children with CP, we decide not to use the usual head-mounted display (HMD) for this purpose. The use of HMD can be hazardous for children because it obstructs their view of the environment, especially when riding an HRS device.
% motion sickness
Numerous researchers \cite{Farmani2018ViewpointReality,Weech2020SensoryCybersickness,Hemmerich2020VisuallyHorizon,Stauffert2020LatencyReview.,Palmisano2020CybersicknessPose} also report another problem of HMD usage: \textit{motion sickness} caused by the inconsistency between the visual input of the eyes and the user movements. This condition can cause nausea, headache, disorientation, and vomiting, which is very dangerous and uncomfortable, especially for children with CP.}

% To avoid obstruction
\textcolor{red}{Considering the problems mentioned before, we built a dome-based VR. By creating a dome-like structure, we can project the VR content to a specialized dome instead of to the HMD. Taking the VR content outside of HMD also eliminates the view obstruction problem and minimizes the risk of motion sickness \cite{Fauzi2017ImplementasiCAVE}. We built our dome-based VR using the design of iDome by Paul Bourke \cite{Bourke2009IDome:Engine}.
% cite iDome by Paul Bourke
The design of iDome is inspired by a planetarium semi-sphere shape. The semi-sphere is cut in half to place the users in front of the dome, not under it. This setup provides a broad immersive view without any obstruction of projection hardware but keeps the user aware of the surroundings.}

% System integration.
% We then integrate the exergaming software, VR dome, HRS machine, and all the necessary equipment to be a whole hippotherapy simulator platform illustrated in Figure \ref{Fig1SystemArchitecture}, providing children fun experiences while giving them the therapy benefit to improve their conditions.

### 2022-11-30 HardwareX - Spectrophotometer/sec2_hwdesc.tex
penambahan template hardwareX

\section{Hardware description}

% Describe the hardware, highlighting the customization rather than the steps of the procedure. Highlight how it differs/which advantage it offers over pre-existing methods. For example, how could this hardware: be compared to other hardware in terms of cost or ease of use, be used in the development of further designs in a particular area, and so on.

% > Add 3-5 bulleted points to broadly explain to other researchers how the hardware could be potentially useful to them, for either standard or novel laboratory tasks, inside or outside of the original user community.

\begin{figure}
	%\begin{adjustwidth}{-\extralength}{0cm}
		%\centering
		\begin{minipage}[b]{11cm}
			\subcaptionbox{}
			{\includesvg[height=5.5cm,inkscapelatex=false]{figs/SystemDesign1}}
		\end{minipage}
		\begin{minipage}[b]{4cm}
			\subcaptionbox{}
			{\includegraphics[height=4.5cm]{figs/FotoSystem}}%
		\end{minipage}%
		%\end{adjustwidth}
		\caption
		{%
			(a) System design diagram. (b) Design implementation in use.
			\label{Fig1Horse}%
		}%
\end{figure}

Describe the hardware, highlighting the customization rather than the steps of the procedure. Highlight how it differs/which advantage it offers over pre-existing methods. For example, how could this hardware: be compared to other hardware in terms of cost or ease of use, be used in the development of further designs in a particular area, and so on. \linebreak \linebreak Add 3-5 bulleted points to broadly explain to other researchers how the hardware could be potentially useful to them, for either standard or novel laboratory tasks, inside or outside of the original user community.
\begin{itemize}[noitemsep, topsep=-2pt]
\item Use of the hardware 1
\item Use of the hardware 2
\item Use of the hardware 3
\end{itemize}

\subsection{Dome Design}
As an Immersive Virtual Environment infrastructure, we
build DOME, for several reasons\\

\noindent $D_g$ = eye height in sitting position (cm) for 7-17 years old

\begin{equation}
    F-measure = 2 * \frac{precision * recall}{precision + recall}
    \label{eq4}
\end{equation}

\noindent with:

\noindent $TP$ = True Positive

### 2022-11-30 HardwareX - Spectrophotometer/sec3_designfiles.tex
penambahan template hardwareX

\section{Design files}

% The  complete  design  files  must  be  either  uploaded  to  an  approved  online  repository,  uploaded  at the  time  of  submission  on  the  online  Editorial  Manager  submission  interface  as  supplementary materials [CAD files, videos,. . . ], or included in the body of the manuscript [e.g.  figures].  The three approved  online  repositories  are  Mendeley  Data,  the  Open  Science  Framework,  and  Zenodo. See repository instructions: https://doi.org/10.5281/zenodo.3346799

% Design files should be in preferred format for making modifications. See OSHWA’s open-source definition for details: https://www.oshwa.org/definition/

for dome design we use, design from paul bourke http://paulbourke.net/dome/iDome/
\textit{The complete design files must be either uploaded to an approved online repository, uploaded at the time of submission on the online \href{https://editorialmanager.com/ohx/}{Editorial Manager} submission interface as supplementary materials [CAD files, videos,\dots], or included in the body of the manuscript [e.g. figures]. The three approved online repositories are \href{https://data.mendeley.com/}{Mendeley Data}, the \href{http://osf.io}{Open Science Framework}, and \href{https://zenodo.org/}{Zenodo}. See repository instructions \href{https://doi.org/10.5281/zenodo.3346799}{here}. Design files should be in preferred format for making modifications. See \href{https://www.oshwa.org/definition/}{OSHWA’s open-source definition} for details.}
\begin{itemize}
\item \textit{CAD files. Authors are encouraged to use free and open source software packages for creating the files. For CAD files, OpenSCAD, FreeCAD, or Blender are encouraged, but if not available source files from proprietary CAD packages such as Autocad or Solidworks and other drawing packages are acceptable.
\item 3D printing. Supplementary files that facilitate the digital replication of the devices are encouraged. For example, STL files for 3-D printing components. We recommend uploading CAD files to the NIH 3D Print Exchange as Custom Labware and providing a link to the location.
\item Electronics. PCB layouts and other electronics design files can be uploaded to the Open Hardware Repository or other repositories.
\item Software and firmware. All software files used in the design and operation of the hardware should be included in the repository. Provide a description of software and firmware and use extensive comments in the code.}
\end{itemize}

%\begin{landscape}
\subsection{Design Files Summary}
% Please include a summary of all design files for your hardware by filling rows of the table below

\tabulinesep=1ex
\begin{tabu} to \linewidth {|X|X|X[1.5,1]|X[1.5,1]|} 
\hline
\textbf{Design file name} & \textbf{File type} & \textbf{Open source license} & \textbf{Location of the file} \\\hline
%Insert design files
\textit{Design file 1} & \textit{e.g. CAD file, figures, videos} & \textit{All designs must be submitted under an open hardware license. Enter the corresponding open source license for the file.} & \textit{Enter a link to the online location or the sentence: ``available with the article'', as appropriate}  \\\hline
\textit{Design file 2} & \dots & \dots & \dots \\\hline
% Design file 3 & File type & License & Link \\\hline
\end{tabu}

% For each design file listed in the summary above, include a short description of the file below (one or two sentences)
\textit{For each design file listed above, include a short description of the file here (one or two sentences)}
%\end{landscape}

### 2022-11-30 HardwareX - Spectrophotometer/sec4_bom.tex
penambahan template hardwareX

\section{Bill of materials}

% For a complex Bill of Materials, the complete Bill of Materials (editable spreadsheet file e.g., ODS file type or PDF file) can be uploaded in an open access online location such as the Open Science Framework repository. Include the link here. Alternatively, the Bill of Materials can be uploaded at the time of submission on the online Elsevier submission interface as supplementary material.

% > To make it easy to tell which item in the Bill of Materials corresponds to which component in your design file(s), use matching designators in both places, or otherwise explain the correspondence.

% > For material type, select from: Metal, semi-conductor, ceramic, polymer, biomaterial, organic, inorganic, composite, nanomaterial, semiconductor, non-specific, or other  
\textit{For a complex Bill of Materials, the complete Bill of Materials (editable spreadsheet file e.g., ODS file type or PDF file) can be uploaded in an open access online location such as the Open Science Framework repository. Include the link here. Alternatively, the Bill of Materials can be uploaded at the time of submission on the online Elsevier submission interface as supplementary material.}
\begin{itemize}
\item \textit{To make it easy to tell which item in the Bill of Materials corresponds to which component in your design file(s), use matching designators in both places, or otherwise explain the correspondence.}
\item \textit{For material type, select from: Metal, semi-conductor, ceramic, polymer, biomaterial, organic, inorganic, composite, nanomaterial, semiconductor, non-specific, or other} 
\end{itemize}

%\begin{landscape}
\tabulinesep=1ex
\begin{tabu} to \linewidth {|l|l|l|l|l|l|l|}
\hline
\textbf{Designator} & \textbf{Component} & \textbf{Number} & \textbf{Cost per unit - USD} & \textbf{Total cost - USD} & \textbf{Source of materials} & \textbf{Material type} \\\hline

%Insert items here
\textit{Designator 1} & \textit{Name of Component 1} & \textit{Number of units} & \textit{Cost per unit} & \textit{Total cost} & \textit{Source} & \textit{Material type} \\\hline
\textit{Designator 2} & \dots & \dots & \dots & \dots & \dots & \dots \\\hline
% Designator 3 & Name of Component 2 & Number of units & Cost per unit & Total cost & Source of materials & Material type \\\hline
\end{tabu}
%\end{landscape}

### 2022-11-30 HardwareX - Spectrophotometer/sec5_buildinstr.tex
penambahan template hardwareX

\section{Build instructions}

%Provide detailed, step by step instructions for the construction of the reported hardware include all necessary information for reproducing the submitted hardware.
% > Explain and, when possible, characterize design decisions. Including design alternatives if they exist. 
% > Use visual instructions such as schematics, images, and videos. 
% > Clearly reference design files and component parts described in the Design File Summary and Bill of Materials. 
% >Highlight potential safety concerns that may arise

\textit{Provide detailed, step by step instructions for the construction of the reported hardware
 include all necessary information for reproducing the submitted hardware.
\begin{itemize}
\item Explain and, when possible, characterize design decisions. Including design alternatives if they exist. 
\item Use visual instructions such as schematics, images, and videos. 
\item Clearly reference design files and component parts described in the Design File Summary and Bill of Materials. 
\item Highlight potential safety concerns that may arise
\end{itemize}}

### 2022-11-30 HardwareX - Spectrophotometer/sec6_operation.tex
penambahan template hardwareX

\section{Operation instructions}

%Provide detailed instructions for the safe and proper operation of the hardware. 
%> Step-by-step operational instructions for operating the hardware. 
%> Use visual instructions as necessary. 
%> Highlight potential safety hazards.

\textit{Provide detailed instructions for the safe and proper operation of the hardware. 
\begin{itemize}
\item Step-by-step operational instructions for operating the hardware. 
\item Use visual instructions as necessary. 
\item Highlight potential safety hazards.
\end{itemize}}

### 2022-11-30 HardwareX - Spectrophotometer/sec7_validation.tex
penambahan template hardwareX

\section{Validation and characterization}

%Demonstrate the operation of the hardware and characterize its performance over relevant critical metrics
%> Demonstrate the use of the hardware for a relevant use case. 
%> If possible, characterize performance of the hardware over operational parameters. 
%> Create a bulleted list that describes the capabilities (and limitations) of the hardware. For example consider descriptions of load, operation time, spin speed, coefficient of variation, accuracy, precision and etc.

\textit{Demonstrate the operation of the hardware and characterize its performance over relevant critical metrics
\begin{itemize}
\item Demonstrate the use of the hardware for a relevant use case. 
\item If possible, characterize performance of the hardware over operational parameters. 
\item Create a bulleted list that describes the capabilities (and limitations) of the hardware. For example consider descriptions of load, operation time, spin speed, coefficient of variation, accuracy, precision and etc. 
\end{itemize}}

### 2022-11-30 HardwareX - Spectrophotometer/sec8_acknow.tex
penambahan template hardwareX

\newpage
\section{Acknowledgements}
This research works was funded by Lembaga Pengembangan Inovasi dan Kewirausahaan, Institut Teknologi Bandung (LPIK ITB) under the grant "Program Penguatan Inovasi 2021" number 289L/IT1.A/SK-KP/2021 and School of Electrical Engineering and Informatics, Institut Teknologi Bandung, under the grant "Program Penelitian, Pengabdian kepada Masyarakat dan Inovasi, Institut Teknologi Bandung, 2021 (P2MI-ITB 2021)" number 917/IT1.C12/KP/2021.

The article processing charge (APC) was funded by School of Electrical Engineering, Telkom University.

### 2022-11-30 paper-kelompok/main.tex
accuracy-glucose

@@
 
-\author{\IEEEauthorblockN{Alzana Armaniar Farhani}
+\author{\IEEEauthorblockN{
+    Alzana Armaniar Farhani\IEEEauthorrefmark{1},
+    Balkan Khilmi Assakandari\IEEEauthorrefmark{2},
+    Anindhita Nayazirly\IEEEauthorrefmark{3}, \\
+    Akhmadi Surawijaya\IEEEauthorrefmark{4},
+    Muhammad Ogin Hasanuddin\IEEEauthorrefmark{5}}
 \IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
-\textit{School of Electrical Engineering} \\
-\textit{and Informatics} \\
+\textit{School of Electrical Engineering and Informatics} \\
 \textit{Institut Teknologi Bandung}\\
 Bandung, Indonesia \\
-farhanialzana@gmail.com}
-\and
-\IEEEauthorblockN{Balkan Khilmi Assakandari}
-\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
-\textit{School of Electrical Engineering} \\
-\textit{and Informatics} \\
-\textit{Institut Teknologi Bandung}\\
-Bandung, Indonesia \\
-balkankhilmi@gmail.com}
-\and
-\IEEEauthorblockN{Anindhita Nayazirly}
-\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
-\textit{School of Electrical Engineering} \\
-\textit{and Informatics} \\
-\textit{Institut Teknologi Bandung}\\
-Bandung, Indonesia \\
-zirlysukarno@gmail.com}
-\newlineauthors
-\IEEEauthorblockN{Akhmadi Surawijaya}
-\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
-\textit{School of Electrical Engineering} \\
-\textit{and Informatics} \\
-\textit{Institut Teknologi Bandung}\\
-Bandung, Indonesia \\
-email}
-\and
-\IEEEauthorblockN{Muhammad Ogin Hasanuddin}
-\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\
-\textit{School of Electrical Engineering} \\
-\textit{and Informatics} \\
-\textit{Institut Teknologi Bandung}\\
-Bandung, Indonesia \\
-email}
+\IEEEauthorrefmark{1}farhanialzana@gmail.com,
+\IEEEauthorrefmark{2}balkankhilmi@gmail.com,
+\IEEEauthorrefmark{3}zirlysukarno@gmail.com,
+email,
+email
+}
 }
@@
 
-The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller.
-The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold.
-If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
-
 \begin{figure}[htbp]
@@
 
-% Pendahuluan
+The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller.
+The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold.
+If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
+
 \section{Results and Discussion}
 \subsection{Accuracy}
+A glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) was used to colorize glucose sample of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+The resulting liquid was then dropped between two microscope slides spaced 1 mm apart as shown in Fig. \ref{mic_slide}.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.8]{mic_slide.png}}
+    \caption{Glucose measurement setup}
+    \label{mic_slide}
+    \end{figure}
+
+Fig.~\ref{glucose_result} shows the measurement results of the glucose experiment with manual baseline correction using linear regression.
+Peak absorbance were measured 0.155 at 519 nm for 40 {\textmu}g/ml and 0.079 at 526 nm for 60 {\textmu}g/ml.
+Absorbance for the 40 {\textmu}g/ml sample turned out higher than the 60 {\textmu}g/ml sample.
+This result does not fit the absorbance-concentration relation of the Beer-Lambert law.
+It was also observed that the 40 {\textmu}g/ml sample appeared darker for the naked eye.
+Thus, a retest of the chemical reactions were due.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.5]{glucose-res.png}}
+    \caption{Glucose absorbance spectrum measurement result, baseline corrected}
+    \label{glucose_result}
+    \end{figure}
+
+Aside from glucose, we have tested the spectrophotometer with food dye measurements.
+Blue, red, and yellow food dyes were mixed with water.
+The volume percentage used were 0.033\%, 0.040\%, 0.050\%, 0.067\%, and 0.100\%.
+The mixture was then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
+The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
+a layer of silicon oil, a layer of stretched parafilm, and a layer of ITO above the droplet.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[angle=90,scale=0.12]{dye-cartridge.jpg}}
+    \caption{Food dye measurement setup}
+    \label{dye_setup}
+    \end{figure}
+
 \subsection{Repeatability}

### 2022-11-30 paper-kelompok/main.tex
accuracy fin

@@
 A glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) was used to colorize glucose sample of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
-The resulting liquid was then dropped between two microscope slides spaced 1 mm apart as shown in Fig. \ref{mic_slide}.
+The resulting liquid was then dropped between two microscope slides spaced 1 mm apart to mimic the light path of the DMF cartridge.
 
-\begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.8]{mic_slide.png}}
-    \caption{Glucose measurement setup}
-    \label{mic_slide}
-    \end{figure}
-
-Fig.~\ref{glucose_result} shows the measurement results of the glucose experiment with manual baseline correction using linear regression.
+Fig.~\ref{glucose_result} shows the measurement results of the glucose experiment with baseline correction using linear regression.
+Manual baseline correction was found necessary because of a voltage fluctuation found between blank measurement and sample measurement.
 Peak absorbance were measured 0.155 at 519 nm for 40 {\textmu}g/ml and 0.079 at 526 nm for 60 {\textmu}g/ml.
@@
 It was also observed that the 40 {\textmu}g/ml sample appeared darker for the naked eye.
-Thus, a retest of the chemical reactions were due.
+Thus, a retest of the chemical reactions was due.
 
@@
 The volume percentage used were 0.033\%, 0.040\%, 0.050\%, 0.067\%, and 0.100\%.
-The mixture was then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
+The samples were then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
 The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
@@
     \end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.6]{dye-res.png}}
+    \caption{Food dye measurement results}
+    \label{dye_res}
+    \end{figure}
+
+Measurements of the food dye samples were regressed as shown in Fig. \ref{dye_res} to create standard curves.
+The wavelengths of which the absorbance were measured were the peak absorbances of each dye.
+An upward trend was found in accordance to the Beer-Lambert law.
+The coefficient of determination measured decreased as the wavelength decreased.
+Accuracy was expected to decrease as wavelength decreases due to weakening lamp emission and camera spectrum response at low wavelengths.
 

### 2022-12-01 paper-kelompok/main.tex
Add Control, User Interface, and Resolution

@@
 
-\subsection{Control Subsystem}
-The subsystems in the spectrophotometer are controlled by a ESP32-S3-WROOM-1-N8 microcontroller module (Espressif Systems, Shanghai, China).
-The task of the control subsystem is to execute the main workflow of the spectrophotometer by a FSM.
+\subsection{Control and Processing Subsystem}
+The control and processing subsystem consists of control and data processing unit.
+Other subsystems in the spectrophotometer are controlled by a ESP32-S3-DevkitC-1 microcontroller board (Espressif Systems, China).
+The task of the control unit is to execute the main workflow of the spectrophotometer by a FSM.
 The control subsystem synchronizes other subsystems, such as the light source with the light sensor when measuring light intensities.
-The subsystem also has non-volatile memory storage to save past absorbance measurements and concentration calibration curves.
+The processing of data signals for measurement processes and results is a responsibility of the data processing unit.
+It converts the sensor's intensity data into an absorbance spectrum (spectrum mode) and performs linear regression to calculate the sample concentration according to the standard samples.
+
+C++ programming was used to create the control subsystem program, and the PlatformIO IDE for Microsoft Visual Studio Code was used (VSCode).
+The primary responsibility of the control unit is to execute the spectrophotometer's processes based on the designed Finite State Machine (FSM), as shown in Fig. \ref{fsm}.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics{control-dfd.png}}
-    \caption{DFD of the control subsystem.}
-    \label{control-dfd}
+    \centerline{\includegraphics{fsm.png}}
+    \caption{FSM diagram of the portable visible spectrophotometer.}
+    \label{fsm}
     \end{figure}
+
+The measurement data are stored on an external SD card that is part of the data processing device.
+The data for the absorbance spectrum and the calibration curves for the quantization mode are tabulated in a CSV-file format.
+The interface between the micro-SD card and the control system is provided by a microSD click module (MikroElektronika, Serbia).
+In order to store calibration values for absorbance measurement and quantization-mode calibration curves, the microcontroller also utilizes its non-volatile memory storage (NVS).
 
@@
 The subsystem also has a function to display measurement data which include sample concentration values, sample absorbance spectrum, regression curves, menus, and settings.
-Fig.
-\ref{ui-dfd} shows the data flow diagram of the user interface subsystem.
+Fig. \ref{ui-dfd} shows the data flow diagram of the user interface subsystem.
 
@@
 \subsection{Wavelength Range}
+\subsection{Resolution}
+Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
+The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
+The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using the following formula:
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.6]{resolution-eq.png}}
+    \label{resolution-eq}
+    \end{figure}
+
 \subsection{Device and DMF Cartridge Distance}
-\subsection{Electronic Display Size}
+
 \subsection{Weight and Size}
+
+\subsection{User Interface}
+The first page of the spectrum-mode measurement instructs the user to insert the blank reference sample into the DMF system.
+The sample input page, which resembles the blank input page, will be on the next page.
+A result page with the peak wavelength and absorbance results will show up after the other subsystems have finished measuring absorbance.
+The user has the option to save the result, return to the main menu, or view the entire spectrum of the absorbance measurement.
+Fig. \ref{lcd-spectrum} illustrates how the spectrum page of the absorbance measurement is shown.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
+    \label{lcd-spectrum}
+    \end{figure}
+
+Quantization-mode measurement starts with a page that displays the list of saved curves.
+Users have the option of using, removing, or adding new curves.
+The user will get a table page if they select an existing curve.
+The table consists of concentration and absorbance values of standard samples, as shown in Fig. \ref{lcd-table}.
+By moving the pointer to the desired absorbance (A) cell and clicking the OK physical button, an absorbance measurement for each concentration value should be made.
+The user will be directed to the blank and sample input page.
+The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
+    \label{lcd-table}
+    \end{figure}
 

### 2022-12-02 paper-kelompok/main.tex
grammar
change equation to latex format

@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics{fsm.png}}
+    \centerline{\includegraphics[scale=0.35]{fsm.png}}
     \caption{FSM diagram of the portable visible spectrophotometer.}
@@
 The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
-The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using the following formula:
+The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using (\ref{resolution}).
 
-    \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{resolution-eq.png}}
-    \label{resolution-eq}
-    \end{figure}
+\begin{equation}
+    resolution=\frac{\lambda_{max} - \lambda_{min}}{n_{pixels}}=\frac{(700 - 400)nm}{393}\approx0.77nm
+    \label{resolution}
+    \end{equation}
 

### 2022-12-04 paper-kelompok/main.tex
dfd scaling
Add conclusion draft and revise FSM diagram

@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.4]{system-dfd.png}}
+    \centerline{\includegraphics[scale=0.27]{system-dfd.png}}
     \caption{Level-1 Data Flow Diagram (DFD) of the system.}
@@
 Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
-The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
-The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using (\ref{resolution}).
+The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, was 297.
+The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using Equation (\ref{resolution}).
 
@@
 \section{Conclusions}
+To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
+The portability makes on-the-go research processes easier.
+Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
+Measurement's accuracy of red, blue, and yellow food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 by Thermo Fisher Scientific).
+The colorimetrice glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by ...
+Future work will focus on...
 

### 2022-12-05 paper-kelompok/main.tex
Minor changes

@@
 \IEEEauthorrefmark{3}zirlysukarno@gmail.com,
-email,
-email
+\IEEEauthorrefmark{4}asurawijaya@itb.ac.id,
+\IEEEauthorrefmark{5}moginh@itb.ac.id
 }
@@
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
-Measurement's accuracy of red, blue, and yellow food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 by Thermo Fisher Scientific).
-The colorimetrice glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by ...
-Future work will focus on...
+Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220).
+The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
+Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.
 

### 2022-12-06 paper-kelompok/main.tex
add ssctp size image

@@
 \subsection{Weight and Size}
+The dimension produced are 120 mm x 131 x 207 mm. 
+Product dimensions are affected by the number of components used in the system and the optical configuration used. 
+The sensor's location, diffraction grating, and light source mainly influence the product's height. 
+The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of ​​the product base. 
+In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[angle=90,scale=0.12]{SCTP_size.png}}
+    \caption{Device's dimensions}
+    \label{device_dimensions}
+    \end{figure}
 

### 2022-12-07 paper-kelompok/main.tex
Add Hardware Assembly subsection

--- 2022-12-05 paper-kelompok/main.tex
@@
 
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.27]{dmf-hardware-scheme.png}}
+    \caption{The main components of the proposed device.}
+    \label{dmf-hardware-scheme}
+    \end{figure}
+
 \subsection{Light Source Subsystem}
@@
 If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
+
+\subsection{Hardware Assembly}
+Using Autodesk Fusion 360 software, the body and individual parts of the portable visible spectrophotometer were created and 3D printed.
+The primary body, the optical light path, and the lamp holder were all 3D printed components.
+Fig.~\ref{hardware} displays internal components of the device.
+A polylactic acid (PLA) filament in black was used due to the need of low light reflectance.
+Electronic parts like printed circuit boards (PCBs) and optical parts were placed inside the main body.
+
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
+    \caption{Overview of the device's internal components.}
+    \label{hardware}
+    \end{figure}
 

### 2022-12-07 paper-kelompok/main.tex
Add UI image captions

@@
     \centerline{\includegraphics[scale=0.27]{system-dfd.png}}
-    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
+    \caption{Level-1 Data Flow Diagram (DFD) of the system}
     \label{system-dfd}
@@
     \centerline{\includegraphics[scale=0.27]{dmf-hardware-scheme.png}}
-    \caption{The main components of the proposed device.}
+    \caption{The main components of the proposed device}
     \label{dmf-hardware-scheme}
@@
     \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
-    \caption{DFD of the light source subsystem.}
+    \caption{DFD of the light source subsystem}
     \label{light-source-dfd}
@@
     \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
-    \caption{DFD of the light sensor subsystem.}
+    \caption{DFD of the light sensor subsystem}
     \label{light-sensor-dfd}
@@
     \centerline{\includegraphics[scale=0.35]{fsm.png}}
-    \caption{FSM diagram of the portable visible spectrophotometer.}
+    \caption{FSM diagram of the portable visible spectrophotometer}
     \label{fsm}
@@
     \centerline{\includegraphics[scale=0.43]{ui-dfd.png}}
-    \caption{DFD of the user interface subsystem.}
+    \caption{DFD of the user interface subsystem}
     \label{ui-dfd}
@@
     \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
-    \caption{DFD of the power subsystem.}
+    \caption{DFD of the power subsystem}
     \label{power-dfd}
@@
     \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
-    \caption{Overview of the device's internal components.}
+    \caption{Overview of the device's internal components}
     \label{hardware}
@@
     \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
+    \caption{The display of the spectrum page of a spectrum-mode measurement}
     \label{lcd-spectrum}
@@
     \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
+    \caption{The display of the table page of a quantization-mode curve}
     \label{lcd-table}

### 2022-12-08 paper-kelompok/main.tex
add SCTP weight

@@
 \subsection{Weight and Size}
-The dimension produced are 120 mm x 131 x 207 mm. 
+Weight measurement is done by placing the product on a digital scale.
+Fig. \ref{device_weight} shows that the product's weight is 0.832 kilograms.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[angle=90,scale=0.12]{SCTP_weight.jpg}}
+    \caption{Device's weight meeasurement}
+    \label{device_weight}
+    \end{figure}
+
+The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
 Product dimensions are affected by the number of components used in the system and the optical configuration used. 

### 2022-12-09 paper-kelompok/main.tex
3 dyes
fig resizings

@@
 The control and processing subsystem consists of control and data processing unit.
-Other subsystems in the spectrophotometer are controlled by a ESP32-S3-DevkitC-1 microcontroller board (Espressif Systems, China).
+Other subsystems in the spectrophotometer are controlled by a ESP32-S3-DevkitC-1 microcontroller board (Espressif Systems, China)/
 The task of the control unit is to execute the main workflow of the spectrophotometer by a FSM.
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
+    \centerline{\includegraphics[scale=0.15]{hardware-2.jpg}}
     \caption{Overview of the device's internal components}
@@
 The volume percentage used were 0.033\%, 0.040\%, 0.050\%, 0.067\%, and 0.100\%.
-The samples were then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
+% The samples were then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
 The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[angle=90,scale=0.12]{dye-cartridge.jpg}}
-    \caption{Food dye measurement setup}
-    \label{dye_setup}
-    \end{figure}
+    \centerline{\includegraphics[scale=0.6]{dye-res.png}}
 
-\begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{dye-res.png}}
-    \caption{Food dye measurement results}
+    \caption{Dye measurement results}
     \label{dye_res}
@@
 Weight measurement is done by placing the product on a digital scale.
-Fig. \ref{device_weight} shows that the product's weight is 0.832 kilograms.
+The product's weight is 0.832 kilograms.
 
-\begin{figure}[htbp]
-    \centerline{\includegraphics[angle=90,scale=0.12]{SCTP_weight.jpg}}
-    \caption{Device's weight meeasurement}
-    \label{device_weight}
-    \end{figure}
+% \begin{figure}[htbp]
+%     \centerline{\includegraphics[scale=0.12]{SCTP_weight.jpg}}
+%     \caption{Device's weight measurement}
+%     \label{device_weight}
+%     \end{figure}
 
@@
 The sensor's location, diffraction grating, and light source mainly influence the product's height. 
-The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of ​​the product base. 
+The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
+The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
 In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[angle=90,scale=0.12]{SCTP_size.png}}
+    \centerline{\includegraphics[scale=0.25]{SCTP_size.png}}
     \caption{Device's dimensions}

### 2022-12-09 paper-kelompok/main.tex
Minor change
Add measuring principles

@@
 
-\section{Methods}
+\section{Materials and Methods}
 \subsection{System Overview}
@@
 
-    \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
-    \caption{DFD of the light source subsystem}
-    \label{light-source-dfd}
-    \end{figure}
-
 \subsection{Light Sensor Subsystem}
@@
 The light sensor subsystem outputs, at maximum, 400 16-bit unsigned integer values, each value representing the light intensity of wavelengths in the visible spectrum range.
-
-    \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
-    \caption{DFD of the light sensor subsystem}
-    \label{light-sensor-dfd}
-    \end{figure}
 
@@
     \end{figure}
+
+The absorbance \emph{A} of a particular sample is computed by the Equation (\ref{absorbance}).
+
+    \begin{equation}
+    A=-\log10{T}=\log{\frac{{I_{0}}{I}}}
+    \label{absorbance}
+    \end{equation}
+
+Transmittance \emph{T} is the percentage of incident radiation that the sample transmits, \emph{I_{0}} denotes the intensity of polychromatic light entering the sample, and \emph{I} denotes the intensity of light leaving the sample;
+Absorbance is directly proportional to the path length \emph{l} through the medium and the concentration \emph{c} of the absorbing substance for monochromatic radiation.
+Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements (\emph{\epsilon} is the molar attenuation coefficient)\cite{b4}.
+
+    \begin{equation}
+    A={\epsilon}{l}{c}
+    \label{beer-lambert}
+    \end{equation}
+
+Beer-Lambert's law states that the concentration of a dilute solution is directly proportional to its absorbance value.
+As a result, in the quantization mode, a linear regression is performed to obtain a slope-intercept form linear equation, as follows.
+
+    \begin{equation}
+    A={m}{c}+{b}
+    \label{linear-eq}
+    \end{equation}
+
+where m is the line's slope (gradient) and b is the constant representing the linear equation's y-intercept.
 
@@
 The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
-The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
 In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
@@
 2019, doi: 10.1007/s42452-019-1693-8.
+\bibitem{b4} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
 \end{thebibliography}

### 2022-12-09 paper-kelompok/main.tex
Modify UI images

@@
 The user has the option to save the result, return to the main menu, or view the entire spectrum of the absorbance measurement.
-Fig. \ref{lcd-spectrum} illustrates how the spectrum page of the absorbance measurement is shown.
+Fig. \ref{lcd-spec} illustrates how the result and spectrum page of the absorbance measurement is shown.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
-    \caption{The display of the spectrum page of a spectrum-mode measurement}
-    \label{lcd-spectrum}
+    \centerline{\includegraphics[scale=0.6]{lcd-spec.JPEG}}
+    \caption{The display of the result pages of a spectrum-mode measurement}
+    \label{lcd-spec}
     \end{figure}
@@
 The user will get a table page if they select an existing curve.
-The table consists of concentration and absorbance values of standard samples, as shown in Fig. \ref{lcd-table}.
+The table consists of concentration and absorbance values of standard samples, as shown in the left side of Fig. \ref{lcd-conc}.
 By moving the pointer to the desired absorbance (A) cell and clicking the OK physical button, an absorbance measurement for each concentration value should be made.
 The user will be directed to the blank and sample input page.
-The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot.
+The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
+    \centerline{\includegraphics[scale=0.6]{lcd-conc.JPEG.}}
     \caption{The display of the table page of a quantization-mode curve}
-    \label{lcd-table}
+    \label{lcd-conc}
     \end{figure}

### 2022-12-09 paper-kelompok/main.tex
add repeatability

--- 2022-12-09 paper-kelompok/main.tex
@@
 \subsection{Repeatability}
+
+The results of 40 ug/ml glucose transmittance measurements in Fig.
+\ref{glucose_transmittance_all} for ten iterations show that the average standard deviation at all wavelengths is 2.58\% with a maximum deviation of 5.28\% and a minimum of 0.87\%.
+As a reference, the standard deviation is also measured at a wavelength of 540 nm, based on the Sigma Aldrich Glucose Assay Kit datasheet.
+The transmittance's standard deviation at 540 nm is 4.09\%.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.25]{glucosetransmittanceALL.png}}
+    \caption{Glucose 40 ug/ml Transmittance}
+    \label{glucose_transmittance_all}
+    \end{figure}
+
+Based on Fig. \ref{glucose_peak_wavelength}, out of 10 measurement iterations, the maximum peak wavelength occurs at 521.76 nm, with the minimum peak wavelength at 519.46 nm.
+On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
+From this data, the standard deviation of the average wavelength is at +0.63 nm, with a maximum deviation of +0.69 nm and a minimum deviation of -1.61.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.25]{glucose_peakwavelength.png}}
+    \caption{Glucose 40 ug/ml Peak Wavelengths}
+    \label{glucose_peak_wavelength}
+    \end{figure}
+
+The wavelength precision and transmittance of the device are affected by several factors. 
+The first factor is the consistency of the internal structure of the product.
+During the implementation and testing process, it was shown that checking or opening the casing for each repair causes a shift in the component. 
+Different lamp position causes other components to block part of the light, causes reduced in intensity for the sample.
+
+From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
+ITO glass should have a holder, for example, given a casing with a clamp. 
+This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause a lens effect\cite{b3}.
+
 \subsection{Wavelength Range}
@@
 Weight measurement is done by placing the product on a digital scale.
-The product's weight is 0.832 kilograms.
-
-% \begin{figure}[htbp]
-%     \centerline{\includegraphics[scale=0.12]{SCTP_weight.jpg}}
-%     \caption{Device's weight measurement}
-%     \label{device_weight}
-%     \end{figure}
-
+The device's weight is 0.832 kilograms. 
 The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
-Product dimensions are affected by the number of components used in the system and the optical configuration used. 
-The sensor's location, diffraction grating, and light source mainly influence the product's height. 
-The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
+Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
+The sensor's location, diffraction grating, and light source mainly influence the device's height. 
+The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the base.
 In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.

### 2022-12-09 paper-kelompok/main.tex
remove

--- 2022-12-09 paper-kelompok/main.tex
@@
 
+    \begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
+    \caption{DFD of the light source subsystem}
+    \label{light-source-dfd}
+    \end{figure}
+
 \subsection{Light Sensor Subsystem}
@@
     \end{figure}
-
-The absorbance \emph{A} of a particular sample is computed by the Equation (\ref{absorbance}).
-
-    \begin{equation}
-    A=-\log10{T}=\log{\frac{{I_{0}}{I}}}
-    \label{absorbance}
-    \end{equation}
-
-Transmittance \emph{T} is the percentage of incident radiation that the sample transmits, \emph{I_{0}} denotes the intensity of polychromatic light entering the sample, and \emph{I} denotes the intensity of light leaving the sample;
-Absorbance is directly proportional to the path length \emph{l} through the medium and the concentration \emph{c} of the absorbing substance for monochromatic radiation.
-Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements (\emph{\epsilon} is the molar attenuation coefficient)\cite{b4}.
-
-    \begin{equation}
-    A={\epsilon}{l}{c}
-    \label{beer-lambert}
-    \end{equation}
-
-Beer-Lambert's law states that the concentration of a dilute solution is directly proportional to its absorbance value.
-As a result, in the quantization mode, a linear regression is performed to obtain a slope-intercept form linear equation, as follows.
-
-    \begin{equation}
-    A={m}{c}+{b}
-    \label{linear-eq}
-    \end{equation}
-
-where m is the line's slope (gradient) and b is the constant representing the linear equation's y-intercept.
 
@@
 \subsection{Repeatability}
-\subsection{Wavelength Range}
 \subsection{Resolution}
@@
 The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
+The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
 In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
@@
 The user has the option to save the result, return to the main menu, or view the entire spectrum of the absorbance measurement.
-Fig. \ref{lcd-spec} illustrates how the result and spectrum page of the absorbance measurement is shown.
+Fig. \ref{lcd-spectrum} illustrates how the spectrum page of the absorbance measurement is shown.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-spec.JPEG}}
-    \caption{The display of the result pages of a spectrum-mode measurement}
-    \label{lcd-spec}
+    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
+    \caption{The display of the spectrum page of a spectrum-mode measurement}
+    \label{lcd-spectrum}
     \end{figure}
@@
 The user will get a table page if they select an existing curve.
-The table consists of concentration and absorbance values of standard samples, as shown in the left side of Fig. \ref{lcd-conc}.
+The table consists of concentration and absorbance values of standard samples, as shown in Fig. \ref{lcd-table}.
 By moving the pointer to the desired absorbance (A) cell and clicking the OK physical button, an absorbance measurement for each concentration value should be made.
 The user will be directed to the blank and sample input page.
-The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
+The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-conc.JPEG.}}
+    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
     \caption{The display of the table page of a quantization-mode curve}
-    \label{lcd-conc}
+    \label{lcd-table}
     \end{figure}
@@
 2019, doi: 10.1007/s42452-019-1693-8.
-\bibitem{b4} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
 \end{thebibliography}

### 2022-12-09 paper-kelompok/main.tex
render

--- 2022-12-09 paper-kelompok/main.tex
@@
     \begin{equation}
-    A=-\log10{T}=\log{\frac{{I_{0}}{I}}}
+    A=-\log10{T}=\log{\frac{I_{0}}{I}}
     \label{absorbance}
@@
 
-Transmittance \emph{T} is the percentage of incident radiation that the sample transmits, \emph{I_{0}} denotes the intensity of polychromatic light entering the sample, and \emph{I} denotes the intensity of light leaving the sample;
-Absorbance is directly proportional to the path length \emph{l} through the medium and the concentration \emph{c} of the absorbing substance for monochromatic radiation.
-Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements (\emph{\epsilon} is the molar attenuation coefficient)\cite{b4}.
+Transmittance $T$ is the percentage of incident radiation that the sample transmits, $I_0$ denotes the intensity of polychromatic light entering the sample, and $I$ denotes the intensity of light leaving the sample;
+Absorbance is directly proportional to the path length $l$ through the medium and the concentration $c$ of the absorbing substance for monochromatic radiation.
+Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b4}.
 
@@
 
-where m is the line's slope (gradient) and b is the constant representing the linear equation's y-intercept.
+where $m$ is the line's slope (gradient) and $b$ is the constant representing the linear equation's y-intercept.
 
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.25]{glucosetransmittanceALL.png}}
+    \centerline{\includegraphics[scale=0.5]{glucosetransmittanceALL.png}}
     \caption{Glucose 40 ug/ml Transmittance}
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.25]{glucose_peakwavelength.png}}
+    \centerline{\includegraphics[scale=0.5]{glucose_peakwavelength.png}}
     \caption{Glucose 40 ug/ml Peak Wavelengths}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-spec.JPEG}}
+    \centerline{\includegraphics[scale=0.06]{lcd-spec.JPEG}}
     \caption{The display of the result pages of a spectrum-mode measurement}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.6]{lcd-conc.JPEG.}}
+    \centerline{\includegraphics[scale=0.06]{lcd-conc.jpeg}}
     \caption{The display of the table page of a quantization-mode curve}

### 2022-12-10 paper-kelompok/main.tex
Grammatical revisions

@@
 Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b3}.
-Droplet mixing allows all chemical reactions to be done on chip.
+Droplet mixing allows chemical reactions to be done on chip.
 An optical detection system needs to be developed in order to measure the absorbance and concentration of a glucose droplet on the DMF chip.
@@
 A light will be emitted through the droplet located on the DMF chip and an array of photodetectors will collect the intensity of incident light.
-A program is uploaded to the system to compute the absorbance and the concentration of the sample droplet.
+A custom program is used in the system to compute the absorbance and the concentration of the sample droplet.
 Users can interact with the system using four input buttons and an LCD which displays the result of the measurements.
 
-The current version of the spectrophotometer has some features as follows:
+Current version of the spectrophotometer has some features as follows:
 \begin{itemize}
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (12cm x 13cm x 20cm)
+    \item Portable (12cm x 13cm x 20cm, 0.832 grams)
 \end{itemize}
@@
 \subsection{Light Source Subsystem}
-The light source subsystem functions to produce polychromatic light as the primary variable to be manipulated and measured by the instrument.
-This subsystem includes 2 modules, namely switching circuits and light sources.
+The light source subsystem's function is to produce polychromatic light as the primary variable to be manipulated and measured by the instrument.
+This subsystem includes two modules, namely switching circuits and a lamp as the light source.
 The process in this subsystem begins with receiving a control signal from the control subsystem to the switching circuit.
-The switching circuit then flows the source voltage to the lamp so that it can be lit.
+Switching circuit is used to turn the light source on and off.
 The polychromatic light source will illuminate and produce light with all UV-Vis frequencies within the specification.
@@
 The control subsystem synchronizes other subsystems, such as the light source with the light sensor when measuring light intensities.
-The processing of data signals for measurement processes and results is a responsibility of the data processing unit.
+Data processing unit's main function is to process data signals for by converting the sensor intensity data into absorbance values.
 It converts the sensor's intensity data into an absorbance spectrum (spectrum mode) and performs linear regression to calculate the sample concentration according to the standard samples.
@@
 C++ programming was used to create the control subsystem program, and the PlatformIO IDE for Microsoft Visual Studio Code was used (VSCode).
-The primary responsibility of the control unit is to execute the spectrophotometer's processes based on the designed Finite State Machine (FSM), as shown in Fig. \ref{fsm}.
+Control unit's function is to execute the spectrophotometer's processes based on the designed Finite State Machine (FSM), as shown in Fig. \ref{fsm}.
 
@@
 For the display, a 3.5-inch non-touchscreen TFT LCD with ILI9488 driver is used.
-The configuration of buttons and non-touchscreen LCD is chosen because it fits the users who use the spectrophotometer using laboratory gloves.
+The configuration of buttons and non-touchscreen LCD is chosen because it fits the users who will use the spectrophotometer using laboratory gloves.
 
@@
 \subsection{Hardware Assembly}
-Using Autodesk Fusion 360 software, the body and individual parts of the portable visible spectrophotometer were created and 3D printed.
-The primary body, the optical light path, and the lamp holder were all 3D printed components.
+To design the casing and individual parts of the spectrophotometer, we used Autodesk Fusion 360 software.
+The 3D-printed body consists of the casing, the optical light path, and the lamp holder.
 Fig.~\ref{hardware} displays internal components of the device.
-A polylactic acid (PLA) filament in black was used due to the need of low light reflectance.
+Polylactic acid (PLA) and acrylonitrile butadiene styrene (ABS) filament colored in black were used due to the need of low light reflectance.
 Electronic parts like printed circuit boards (PCBs) and optical parts were placed inside the main body.
@@
 \subsection{Accuracy}
-A glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) was used to colorize glucose sample of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+Glucose samples are prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
 The resulting liquid was then dropped between two microscope slides spaced 1 mm apart to mimic the light path of the DMF cartridge.
@@
 Manual baseline correction was found necessary because of a voltage fluctuation found between blank measurement and sample measurement.
-Peak absorbance were measured 0.155 at 519 nm for 40 {\textmu}g/ml and 0.079 at 526 nm for 60 {\textmu}g/ml.
+Value of 0.155 peak absorbance were detected at 519 nm for 40 {\textmu}g/ml and 0.079 at 526 nm for 60 {\textmu}g/ml.
 Absorbance for the 40 {\textmu}g/ml sample turned out higher than the 60 {\textmu}g/ml sample.
@@
 
-\subsection{Wavelength Range}
 \subsection{Resolution}
@@
 
-\subsection{Device and DMF Cartridge Distance}
-
 \subsection{Weight and Size}
-Weight measurement is done by placing the product on a digital scale.
+Weight measurement is done by placing the device on a digital scale.
 The device's weight is 0.832 kilograms. 
-The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
+The final dimension of the spectrophotometer are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
 Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
@@
 
+\section*{Acknowledgement}
+
 \section*{References}

### 2022-12-10 paper-kelompok/main.tex
Add references and modify UI images

@@
 These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic instrumentation, such as HPLC systems.
-While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well.
+While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
 However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
@@
 Various colorimetric methods involving reactions with different enzymes for glucose measurement are the object of research being developed to obtain colorimetric methods that are accurate, sensitive, selective, and inexpensive.
-Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H2O2).
-In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b1}.
+There are several enzymes that take glucose as a substrate and turn it into a product or byproduct that can be measured or detected.
+In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b1}.
+Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H_2O_2).
+In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b2}.
 
-Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means.
+Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means\cite{b3,b4}.
 One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems.
-The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b2}.
+The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b3}.
 The DMF system mainly consists of a fluid layer located between the top and bottom plates.
-Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b3}.
+Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b5}.
 Droplet mixing allows chemical reactions to be done on chip.
@@
 Absorbance is directly proportional to the path length $l$ through the medium and the concentration $c$ of the absorbing substance for monochromatic radiation.
-Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b4}.
+Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b6}.
 
@@
 \subsection{Accuracy}
-Glucose samples are prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+Glucose samples are prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b6}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
 The resulting liquid was then dropped between two microscope slides spaced 1 mm apart to mimic the light path of the DMF cartridge.
@@
 \begin{thebibliography}{00}
-\bibitem{b1} H.
+\bibitem{b1} A. L. Galant, R. C. Kaufman, and J. D. Wilson, “Glucose: Detection and analysis,” Food Chemistry, vol. 188, pp. 149–160, 2015. 
+\bibitem{b2} H.
 V.
@@
 2020, doi: 10.1016/j.arabjc.2020.05.008.
-\bibitem{b2} Z.
+\bibitem{b3} Z.
 Gu, M.
@@
 11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
-\bibitem{b3} S.
+\bibitem{b4} R.
+B.
+Fair, A.
+Khlystov, V.
+Srinivasan, V.
+K.
+Pamula, and K.
+N.
+Weaver, “Integrated Chemical/biochemical sample collection, pre-concentration, and analysis on a digital microfluidic lab-on-a-chip platform,” SPIE Proceedings, 2004.
+\bibitem{b5} S.
 Huang and R.
@@
 2019, doi: 10.1007/s42452-019-1693-8.
-\bibitem{b4} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
+\bibitem{b6} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
+\bibitem{b7} B. E. Raabo and T. C. Terkildsen, “On the enzymatic determination of blood glucose,” Scandinavian Journal of Clinical and Laboratory Investigation, vol. 12, no. 4, pp. 402–407, 1960. 
 \end{thebibliography}

### 2022-12-10 paper-kelompok/main.tex
accuracy analysis

@@
 In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b1}.
-Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H_2O_2).
+Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide ($H_2O_2$).
 In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b2}.
@@
 \subsection{Accuracy}
-Glucose samples are prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b6}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
-The resulting liquid was then dropped between two microscope slides spaced 1 mm apart to mimic the light path of the DMF cartridge.
+Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b6}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
 
@@
 Aside from glucose, we have tested the spectrophotometer with food dye measurements.
-Blue, red, and yellow food dyes were mixed with water.
-The volume percentage used were 0.033\%, 0.040\%, 0.050\%, 0.067\%, and 0.100\%.
-% The samples were then dropped to the DMF cartridge as shown in Fig. \ref{dye_setup}.
-The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
-a layer of silicon oil, a layer of stretched parafilm, and a layer of ITO above the droplet.
+Blue (630 nm peak), red (508 nm peak), and yellow (427 nm peak) food dyes were mixed with water.
+The volume percentage used were 0.033\%, 0.040\%, 0.050\%, and 0.067\%.
+The device's measurements are shown in Fig. \ref{dye_res}.
+The device's measured transmittance spectra was compared to the transmittance spectra from a commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific).
+The average transmittance spectrum RMSE obtained was 11.22\%.
+Peak wavelength errors were $+0.99$ nm, $-1.05$ nm, and $+29.71$ nm for blue, red, and yellow dyes respectively.
+
+The biggest error factor for transmittance was the shift in the baseline.
+The device measured numerous instances of negative absorbance.
+A negative absorbance is the result of a transmittance higher than 100\%; the blank intensity readout was higher than the sample intensity readout.
+In other words, the sensor deemed the blank (water) brighter than the sample.
+This could happen when the intensity from the light source was brighter for the sample than the blank.
+The voltage log confirmed this hypothesis.
+A blank measurement took longer time than a sample measurement.
+The longer a measurement took, the lower the power dropped, and the lower intensity was readout.
+
+The significant increase of the peak wavelength error for the yellow dye was caused by the spectrum response of the system.
+The yellow dye was evaluated at its peak absorbance wavelength of 427 nm.
+The pixel spectrum response in 400 nm is 45\% the spectrum response in 550 nm.
+Moreover, the lamp emission in 400 nm is 50\% the lamp emission in 700 nm.
+These effeciency drops resulted in low intensity readouts for blank measurements, which increased resolution and noise.
+Increasing the lamp power was not an option because the heat would damage the plastic structures of the light path.
 
@@
 
-\section*{References}
-
 \begin{thebibliography}{00}

### 2022-12-10 paper-kelompok/main.tex
schematics and ack

@@
 Currently, various methods detect and measure glucose concentrations in food matrices.
-These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic instrumentation, such as HPLC systems.
+These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic approaches, such as HPLC systems.
 While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
+    \centerline{\includegraphics[scale=0.3]{power-schematic.png}}
     \caption{DFD of the power subsystem}
@@
 \section*{Acknowledgement}
+The authors thank Dr. Isa Anshori from Department of Biomedical Engineering, Institut Teknologi Bandung and his research team for assistance with DMF integration and sample preparation.
+This work was funded by Department of Electrical Engineering, Institut Teknologi Bandung.
 

### 2022-12-10 paper-kelompok/main.tex
Acknowledgement & keywords

--- 2022-12-10 paper-kelompok/main.tex
@@
 \begin{abstract}
-    Instrumen yang telah dikembangkan kelompok Tugas Akhir Teknik Elektro sebelumnya adalah sebuah spektrofotometer portabel yang dapat bekerja pada spektrum gelombang ultraviolet dan cahaya tampak, atau umumnya disebut spektrofotometer UV-Vis.
-Spektrofotometer yang dibuat hanya dapat melakukan perhitungan intensitas cahaya secara relatif terhadap nilai intensitas tertinggi yang terukur, tidak dilakukan kalibrasi skala panjang gelombang dan tuning fungsi konversi citra.
-Hal ini menunjukkan bahwa pengukuran yang dilakukan masih bersifat kualitatif.
-Spektrofotometer yang telah dikembangkan kelompok Tugas Akhir Teknik Elektro belum memiliki kapabilitas untuk
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-    UV-VIS Spectrophotometry
+    Spectrophotometry, Droplets, Portable, Digital microfluidics
 \end{IEEEkeywords}
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (12cm x 13cm x 20cm, 0.832 grams)
+    \item Portable (120 x 131 x 207 mm, 0.832 grams)
 \end{itemize}
@@
 The cartridge consisted of a DMF cartridge PCB, a layer of stretched parafilm, and a layer of silicon oil underneath the droplet;
-a layer of silicon oil, a layer of stretched parafilm, and a layer of ITO above the droplet.
+a layer of silicon oil, a layer of stretched parafilm, and a layer of indium-tin oxide (ITO) coated glass above the droplet.
 
@@
 ITO glass should have a holder, for example, given a casing with a clamp. 
-This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause a lens effect\cite{b3}.
+This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause a lens effect\cite{b5}.
 
@@
 The device's weight is 0.832 kilograms. 
-The final dimension of the spectrophotometer are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
+The final dimension of the spectrophotometer are 120 x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
 Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
@@
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
-Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220).
+Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Thermo Scientific™ Evolution 220).
 The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
@@
 \section*{Acknowledgement}
+This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
+The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
 

### 2022-12-10 paper-kelompok/main.tex

--- 2022-12-10 paper-kelompok/main.tex
@@
 \section*{Acknowledgement}
-The authors thank Dr. Isa Anshori from Department of Biomedical Engineering, Institut Teknologi Bandung and his research team for assistance with DMF integration and sample preparation.
-This work was funded by Department of Electrical Engineering, Institut Teknologi Bandung.
+This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
+The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
+
+\section*{References}
 

### 2022-12-10 paper-kelompok/main.tex
Minor changes

@@
 \subsection{Accuracy}
-Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b6}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
 The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
@@
 The device's measurements are shown in Fig. \ref{dye_res}.
-The device's measured transmittance spectra was compared to the transmittance spectra from a commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific).
+The device's measured transmittance spectra was compared to the transmittance spectra from a commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
 The average transmittance spectrum RMSE obtained was 11.22\%.
@@
 
-From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
+From several tests, the treatment of the indium-tin oxide (ITO) coated glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
 ITO glass should have a holder, for example, given a casing with a clamp. 
@@
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
-Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Thermo Scientific™ Evolution 220).
+Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
 The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.

### 2022-12-10 paper-kelompok/main.tex
abstract

--- 2022-12-10 paper-kelompok/main.tex
@@
 \begin{abstract}
-
+We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
+An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
+The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
+The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
+The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
+The results showed generally good performance compared with a research-grade commercial spectrophotometer.
 \end{abstract}
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (120 x 131 x 207 mm, 0.832 grams)
+    \item Portable (120 x 131 x 207 mm, 2 kg)
 \end{itemize}
@@
 The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit. 
-The battery can be recharged easily whenever the battery voltage is insufficient.
+The battery can be recharged with a 12V adapter whenever the battery voltage is insufficient. 
 The power subsystem also provides information about the battery voltage value to be displayed to the user.
@@
 
-The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller.
-The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold.
+The power from the adapter is converted into 8.4V (full capacity) using a charging module when charging is needed.
+The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6V output to the microcontroller and other loads.
 If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
@@
 \section{Conclusions}
-To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
-The portability makes on-the-go research processes easier.
+To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
@@
 The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
-Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.
+Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.
 
 \section*{Acknowledgement}
-This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
-The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
-
-\section*{References}
+The authors thank Dr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
+This work was funded by the Department of Electrical Engineering, Institut Teknologi Bandung.
 

### 2022-12-10 paper-kelompok/main.tex
rev2

@@
 The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
-The results showed generally good performance compared with a research-grade commercial spectrophotometer.
+The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
+The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
 \end{abstract}
@@
 On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
-From this data, the standard deviation of the average wavelength is at +0.63 nm, with a maximum deviation of +0.69 nm and a minimum deviation of -1.61.
+From this data, the standard deviation of the average wavelength is at 0.63 nm, with a minimum deviation of 0.69 nm and a minimum deviation of 1.61 nm.
 

### 2022-12-10 paper-kelompok/main.tex
updated caption schematic

@@
 \begin{abstract}
-We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
+We propose a portable visible spectrophotometer with an ability to integrate with a digital microfluidic (DMF) system.
 An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
-The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
+The device had a dimension of 120 x 131 x 207 mm and a weight of 832 g.
 The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
@@
     \centerline{\includegraphics[scale=0.3]{power-schematic.png}}
-    \caption{DFD of the power subsystem}
+    \caption{Schematic of the power subsystem}
     \label{power-dfd}

### 2022-12-10 paper-kelompok/main.tex
Replace UI images with  a better-resolution ones

--- 2022-12-10 paper-kelompok/main.tex
@@
 
-\title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}
+\title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System}
 
@@
 \begin{abstract}
-We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
-An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
-The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
-The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
-The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
-The results showed generally good performance compared with a research-grade commercial spectrophotometer.
+
 \end{abstract}
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (120 x 131 x 207 mm, 2 kg)
+    \item Portable (120 x 131 x 207 mm, 0.832 grams)
 \end{itemize}
@@
 The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit.
-The battery can be recharged with a 12V adapter whenever the battery voltage is insufficient. 
+The battery can be recharged easily whenever the battery voltage is insufficient.
 The power subsystem also provides information about the battery voltage value to be displayed to the user.
@@
 
-The power from the adapter is converted into 8.4V (full capacity) using a charging module when charging is needed.
-The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6V output to the microcontroller and other loads.
+The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller.
+The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold.
 If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-spec.JPEG}}
+    \centerline{\includegraphics[scale=0.06]{lcd-spec.png}}
     \caption{The display of the result pages of a spectrum-mode measurement}
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-conc.jpeg}}
+    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
     \caption{The display of the table page of a quantization-mode curve}
@@
 \section{Conclusions}
-To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
+To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
+The portability makes on-the-go research processes easier.
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
@@
 The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
-Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.
+Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.
 
 \section*{Acknowledgement}
-The authors thank Dr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
-This work was funded by the Department of Electrical Engineering, Institut Teknologi Bandung.
+This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
+The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
+
+\section*{References}
 

### 2022-12-10 paper-kelompok/main.tex
Minor caption change

--- 2022-12-10 paper-kelompok/main.tex
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-conc.jpeg}}
-    \caption{The display of the table page of a quantization-mode curve}
+    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
+    \caption{The display of the table and plot page of a quantization-mode curve}
     \label{lcd-conc}

### 2022-12-10 paper-kelompok/main.tex
Minor changes

@@
 Other subsystems in the spectrophotometer are controlled by a ESP32-S3-DevkitC-1 microcontroller board (Espressif Systems, China)/
-The task of the control unit is to execute the main workflow of the spectrophotometer by a FSM.
+The task of the control unit is to execute the main workflow of the spectrophotometer by a Finite State Machine (FSM).
 The control subsystem synchronizes other subsystems, such as the light source with the light sensor when measuring light intensities.
@@
 C++ programming was used to create the control subsystem program, and the PlatformIO IDE for Microsoft Visual Studio Code was used (VSCode).
-Control unit's function is to execute the spectrophotometer's processes based on the designed Finite State Machine (FSM), as shown in Fig. \ref{fsm}.
+Control unit's function is to execute the spectrophotometer's processes based on the designed FSM, as shown in Fig. \ref{fsm}.
 
@@
 
-The absorbance \emph{A} of a particular sample is computed by the Equation (\ref{absorbance}).
+The absorbance $A$ of a particular sample is computed by the Equation (\ref{absorbance}).
 

### 2022-12-10 paper-kelompok/main.tex
Minor typo change

@@
 \subsection{Accuracy}
-Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml concentration.
+Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
 The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.

### 2022-12-10 paper-kelompok/main.tex
fixed accuracy analysis

@@
 The device measured numerous instances of negative absorbance.
-A negative absorbance is the result of a transmittance higher than 100\%; the blank intensity readout was higher than the sample intensity readout.
-In other words, the sensor deemed the blank (water) brighter than the sample.
-This could happen when the intensity from the light source was brighter for the sample than the blank.
+A negative absorbance is the result of a transmittance higher than 100\%.
+Transmittance is defined as $T=I_{sample}/I_{blank}$, which means the blank intensity readout was lower than the sample intensity readout.
+In other words, the sensor deemed the blank (water) darker than the sample.
+This could happen when the intensity from the light source was darker for the blank than the sample.
 The voltage log confirmed this hypothesis.
 A blank measurement took longer time than a sample measurement.
-The longer a measurement took, the lower the power dropped, and the lower intensity was readout.
+The longer a measurement took time, the lower the power dropped, and the lower the intensity was read.
 

### 2022-12-11 paper-kelompok/main.tex
grammar fix
rev2

@@
 We propose a portable visible spectrophotometer with an ability to integrate with a digital microfluidic (DMF) system.
-An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
-The device had a dimension of 120 x 131 x 207 mm and a weight of 832 g.
+An interface which consists of an LCD and a set of buttons allows users to gather and view measurement results in a continous manner.
+The device had a dimension of 120 x 131 x 207 mm\textsuperscript{3} with the weight of 0.832 kg.
 The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
 The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
-The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
+The transmittance error was ±11.22\% with ±9.88 nm wavelength error.
 The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
@@
 
-Current version of the spectrophotometer has some features as follows:
+The spectrophotometer was designed to satisfy several features as follows:
 \begin{itemize}
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (120 x 131 x 207 mm, 2 kg)
+    \item Portable (should be smaller than 420 x 300 x 180 mm\textsuperscript{3} and weighs less than 2 kg)
 \end{itemize}
@@
 \subsection{System Overview}
-The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem.
-Its data flow diagram (DFD) is shown in Fig.
-\ref{system-dfd}.
-The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector.
+The proposed system consists of five subsystems which are light source, light sensor, control and processing system, user interface, and power subsystem.
+Its data flow diagram (DFD) is shown in Fig. \ref{system-dfd}. The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector.
 The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform.
@@
 The grating has a groove density of 1200 lines/mm, and the first order of diffraction is used to separate the visible spectrum.
-The resulting ray is then recorded by a CMOS image sensor (Arducam MT9M001 Monochrome Camera Module).
+The diffracted ray is then recorded by a CMOS image sensor (Arducam MT9M001 Monochrome Camera Module).
 Different pixel of the image sensor captures the intensity of different wavelengths ranging from 400 nanometer to 700 nanometer formatted into 10-bit unsigned integer.
@@
 C++ programming was used to create the control subsystem program, and the PlatformIO IDE for Microsoft Visual Studio Code was used (VSCode).
-Control unit's function is to execute the spectrophotometer's processes based on the designed FSM, as shown in Fig. \ref{fsm}.
+Control unit's function is to execute the spectrophotometer's processes based on the designed FSM as shown in Fig. \ref{fsm}.
 
@@
 Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
-The resulting liquid was then dropped between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
+The resulting liquid was then placed between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
 
@@
 Absorbance for the 40 {\textmu}g/ml sample turned out higher than the 60 {\textmu}g/ml sample.
-This result does not fit the absorbance-concentration relation of the Beer-Lambert law.
+This result does not fit the absorbance-concentration relation of the Beer-Lambert's law.
 It was also observed that the 40 {\textmu}g/ml sample appeared darker for the naked eye.
@@
 Blue (630 nm peak), red (508 nm peak), and yellow (427 nm peak) food dyes were mixed with water.
-The volume percentage used were 0.033\%, 0.040\%, 0.050\%, and 0.067\%.
+The volume percentages used were 0.033\%, 0.040\%, 0.050\%, and 0.067\%.
 The device's measurements are shown in Fig. \ref{dye_res}.
@@
 A blank measurement took longer time than a sample measurement.
-The longer a measurement took time, the lower the power dropped, and the lower the intensity was read.
+The longer a measurement took time, the lower the power dropped, hence the lower the intensity became.
 
@@
 The yellow dye was evaluated at its peak absorbance wavelength of 427 nm.
-The pixel spectrum response in 400 nm is 45\% the spectrum response in 550 nm.
-Moreover, the lamp emission in 400 nm is 50\% the lamp emission in 700 nm.
-These effeciency drops resulted in low intensity readouts for blank measurements, which increased resolution and noise.
+The pixel spectrum response in 400 nm is 45\% the response in 550 nm.
+Moreover, the lamp emission in 400 nm is 50\% the emission in 700 nm.
+These effeciency drops caused low intensity readouts, which increased resolution and noise in lower wavelengths (400 to 450 nm).
 Increasing the lamp power was not an option because the heat would damage the plastic structures of the light path.
@@
 Measurements of the food dye samples were regressed as shown in Fig. \ref{dye_res} to create standard curves.
-The wavelengths of which the absorbance were measured were the peak absorbances of each dye.
-An upward trend was found in accordance to the Beer-Lambert law.
-The coefficient of determination measured decreased as the wavelength decreased.
-Accuracy was expected to decrease as wavelength decreases due to weakening lamp emission and camera spectrum response at low wavelengths.
+The wavelengths of which the absorbances were measured were the peak absorbances of each dye.
+An upward trend was found in accordance to the Beer-Lambert's law.
 
@@
 On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
-From this data, the standard deviation of the average wavelength is at 0.63 nm, with a minimum deviation of 0.69 nm and a minimum deviation of 1.61 nm.
+From this data, the average wavelength standard deviation is at 0.63 nm, with a minimum deviation of 0.69 nm and a maximum deviation of 1.61 nm.
 
@@
 The first factor is the consistency of the internal structure of the product.
-During the implementation and testing process, it was shown that checking or opening the casing for each repair causes a shift in the component. 
-Different lamp position causes other components to block part of the light, causes reduced in intensity for the sample.
+During the implementation and testing process, it was shown that checking or opening the casing for each for each adjustment done for troubleshooting causes a shift in the component. 
+Light pathway obscured by other components cause a reduction in the light intensity which pass through the sample.
 
-From several tests, the treatment of the indium-tin oxide (ITO) coated glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
+From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
 ITO glass should have a holder, for example, given a casing with a clamp. 
-This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause a lens effect\cite{b5}.
+This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.
 
@@
 \subsection{Weight and Size}
-Weight measurement is done by placing the device on a digital scale.
-The device's weight is 0.832 kilograms. 
-The final dimension of the spectrophotometer are 120 x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
+Weight measurement is done by placing the device on a digital scale which shows the weight is 0.832 kilograms. 
+The final dimension of the spectrophotometer are 120 x 131 x 207 mm\textsuperscript{3}, as shown in Fig. \ref{device_dimensions}
 Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
 The sensor's location, diffraction grating, and light source mainly influence the device's height. 
-The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the base.
-In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
+The battery has a size of 70 x 42 x 21 mm\textsuperscript{3}, which significantly affects the determination of the minimum area of the base.
+In addition, the button component with a diagonal position uses a large enough area but leaves some empty space.
 
@@
     \centerline{\includegraphics[scale=0.06]{lcd-spec.png}}
-    \caption{The display of the result pages of a spectrum-mode measurement}
+    \caption{The display of the result (left) and spectrum (right) page of a spectrum-mode measurement}
     \label{lcd-spec}
@@
 
-Quantization-mode measurement starts with a page that displays the list of saved curves.
-Users have the option of using, removing, or adding new curves.
+Quantization-mode measurement starts with a display page that shows the list of saved curves.
+Users have the option of using, removing, or adding new curve data.
 The user will get a table page if they select an existing curve.
@@
 The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
+There are six curve slots available and each curve can store up to 10 sets of concentration and absorbance values.
 
@@
     \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
-    \caption{The display of the table and plot page of a quantization-mode curve}
+    \caption{The display of the table (left) and plot (right) page of a quantization-mode curve}
     \label{lcd-conc}
@@
 \section{Conclusions}
-To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
+To support the study of spectrophotometry analysis in DMF platform, we have designed and assembled of a portable visible spectrophotometer that can be integrated with a particular DMF system.
 Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
 Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
-The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
+The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable at certain degree but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
 Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.

### 2022-12-11 paper-kelompok/main.tex
Grammatical revision (Rev 2)

@@
 An interface which consists of an LCD and a set of buttons allows users to gather and view measurement results in a continous manner.
-The device had a dimension of 120 x 131 x 207 mm\textsuperscript{3} with the weight of 0.832 kg.
+The device had a dimension of 120 x 131 x 207 mmˆ3 with the weight of 0.832 kg.
 The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
 The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
-The transmittance error was ±11.22\% with ±9.88 nm wavelength error.
+The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
 The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (should be smaller than 420 x 300 x 180 mm\textsuperscript{3} and weighs less than 2 kg)
+    \item Portable (should be smaller than 420 x 300 x 180 mmˆ3 and weighs less than 2 kg)
 \end{itemize}
@@
 Absorbance for the 40 {\textmu}g/ml sample turned out higher than the 60 {\textmu}g/ml sample.
-This result does not fit the absorbance-concentration relation of the Beer-Lambert's law.
+This result does not fit the absorbance-concentration relation of the Beer-Lambert law.
 It was also observed that the 40 {\textmu}g/ml sample appeared darker for the naked eye.
@@
 Blue (630 nm peak), red (508 nm peak), and yellow (427 nm peak) food dyes were mixed with water.
-The volume percentages used were 0.033\%, 0.040\%, 0.050\%, and 0.067\%.
+The volume percentage used were 0.033\%, 0.040\%, 0.050\%, and 0.067\%.
 The device's measurements are shown in Fig. \ref{dye_res}.
@@
 A blank measurement took longer time than a sample measurement.
-The longer a measurement took time, the lower the power dropped, hence the lower the intensity became.
+The longer a measurement took time, the lower the power dropped, and the lower the intensity was read.
 
@@
 The yellow dye was evaluated at its peak absorbance wavelength of 427 nm.
-The pixel spectrum response in 400 nm is 45\% the response in 550 nm.
-Moreover, the lamp emission in 400 nm is 50\% the emission in 700 nm.
-These effeciency drops caused low intensity readouts, which increased resolution and noise in lower wavelengths (400 to 450 nm).
+The pixel spectrum response in 400 nm is 45\% the spectrum response in 550 nm.
+Moreover, the lamp emission in 400 nm is 50\% the lamp emission in 700 nm.
+These effeciency drops caused low intensity readouts for blank measurements, which increased resolution and noise in lower wavelengths.
 Increasing the lamp power was not an option because the heat would damage the plastic structures of the light path.
@@
 Measurements of the food dye samples were regressed as shown in Fig. \ref{dye_res} to create standard curves.
-The wavelengths of which the absorbances were measured were the peak absorbances of each dye.
-An upward trend was found in accordance to the Beer-Lambert's law.
+The wavelengths of which the absorbance were measured were the peak absorbances of each dye.
+An upward trend was found in accordance to the Beer-Lambert law.
+The coefficient of determination measured decreased as the wavelength decreased.
+Accuracy was expected to decrease as wavelength decreases due to weakening lamp emission and camera spectrum response at low wavelengths.
 
@@
 On average, the peak wavelength that occurs is 521.07 nm, indicated by a black line on the graph.
-From this data, the average wavelength standard deviation is at 0.63 nm, with a minimum deviation of 0.69 nm and a maximum deviation of 1.61 nm.
+From this data, the standard deviation of the average wavelength is at 0.63 nm, with a minimum deviation of 0.69 nm and a minimum deviation of 1.61 nm.
 
@@
 The first factor is the consistency of the internal structure of the product.
-During the implementation and testing process, it was shown that checking or opening the casing for each for each adjustment done for troubleshooting causes a shift in the component. 
-Light pathway obscured by other components cause a reduction in the light intensity which pass through the sample.
+During the implementation and testing process, it was shown that for each adjustment done for troubleshooting causes a shift in the component. 
+Light pathway obscured by other components cause a reduction in the light intensity which passes through the sample.
 
-From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
+From several tests, the treatment of the indium-tin oxide (ITO) coated glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
 ITO glass should have a holder, for example, given a casing with a clamp. 
-This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.
+This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b5}.
 
@@
 \subsection{Weight and Size}
-Weight measurement is done by placing the device on a digital scale which shows the weight is 0.832 kilograms. 
-The final dimension of the spectrophotometer are 120 x 131 x 207 mm\textsuperscript{3}, as shown in Fig. \ref{device_dimensions}
+Weight measurement is done by placing the device on a digital scale which shows the weight of 0.832 kilograms. 
+The final dimension of the spectrophotometer are 120 x 131 x 207 mmˆ3, as shown in Fig. \ref{device_dimensions}
 Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
 The sensor's location, diffraction grating, and light source mainly influence the device's height. 
-The battery has a size of 70 x 42 x 21 mm\textsuperscript{3}, which significantly affects the determination of the minimum area of the base.
+The battery has a size of 70 x 42 x 21 mmˆ3, which significantly affects the determination of the minimum area of the base.
 In addition, the button component with a diagonal position uses a large enough area but leaves some empty space.
@@
 The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
-There are six curve slots available and each curve can store up to 10 sets of concentration and absorbance values.
+Each curve can store up to 10 sets of concentration and absorbance values.
 

### 2022-12-12 paper-kelompok/main.tex
Minor change
Add a paragraph for intro

@@
 \section{Introduction}
-Currently, various methods detect and measure glucose concentrations in food matrices.
+The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluid.
+The number of people suffering from diabetes is rising, and there is over 1 in 10 adults are affected worldwide.
+By 2045, 780 million people worldwide are predicted to live with diabetes\cite{b1}.
+Diabetes patients are at a higher risk of critical health problems than non-diabetic individuals.
+As a result, accurate monitoring of blood glucose concentrations in diabetic patients is crucial for real-time diabetes diagnosis.
+
+Currently, various methods detect and measure glucose concentrations.
 These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic approaches, such as HPLC systems.
-While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
+While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b2}.
 However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
@@
 There are several enzymes that take glucose as a substrate and turn it into a product or byproduct that can be measured or detected.
-In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b1}.
+In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b2}.
 Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide ($H_2O_2$).
-In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b2}.
+In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b3}.
 
-Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means\cite{b3,b4}.
+Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means\cite{b4,b5}.
 One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems.
-The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b3}.
+The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b4}.
 The DMF system mainly consists of a fluid layer located between the top and bottom plates.
-Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b5}.
+Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b6}.
 Droplet mixing allows chemical reactions to be done on chip.
@@
 Absorbance is directly proportional to the path length $l$ through the medium and the concentration $c$ of the absorbing substance for monochromatic radiation.
-Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b6}.
+Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b7}.
 
@@
 The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit. 
-The battery can be recharged with a 12V adapter whenever the battery voltage is insufficient. 
+The battery can be recharged with a 12 V adapter whenever the battery voltage is insufficient. 
 The power subsystem also provides information about the battery voltage value to be displayed to the user.
@@
 
-The power from the adapter is converted into 8.4V (full capacity) using a charging module when charging is needed.
-The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6V output to the microcontroller and other loads.
+The power from the adapter is converted into 8.4 V (full capacity) using a charging module when charging is needed.
+The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4 V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6 V output to the microcontroller and other loads.
 If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
@@
 \subsection{Accuracy}
-Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
+Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b8}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
 The resulting liquid was then placed between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
@@
 The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
-Each curve can store up to 10 sets of concentration and absorbance values.
+There are six curve slots available and each curve can store up to 10 sets of concentration and absorbance values.
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} A. L. Galant, R. C. Kaufman, and J. D. Wilson, “Glucose: Detection and analysis,” Food Chemistry, vol. 188, pp. 149–160, 2015. 
-\bibitem{b2} H.
+\bibitem{b1} “IDF Diabetes Atlas Tenth edition.” [Online]. Available: https://diabetesatlas.org/. [Accessed: 12-Dec-2022]. 
+\bibitem{b2} A. L. Galant, R. C. Kaufman, and J. D. Wilson, “Glucose: Detection and analysis,” Food Chemistry, vol. 188, pp. 149–160, 2015. 
+\bibitem{b3} H.
 V.
@@
 2020, doi: 10.1016/j.arabjc.2020.05.008.
-\bibitem{b3} Z.
+\bibitem{b4} Z.
 Gu, M.
@@
 11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
-\bibitem{b4} R.
+\bibitem{b5} R.
 B.
@@
 Weaver, “Integrated Chemical/biochemical sample collection, pre-concentration, and analysis on a digital microfluidic lab-on-a-chip platform,” SPIE Proceedings, 2004.
-\bibitem{b5} S.
+\bibitem{b6} S.
 Huang and R.
@@
 2019, doi: 10.1007/s42452-019-1693-8.
-\bibitem{b6} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
-\bibitem{b7} B. E. Raabo and T. C. Terkildsen, “On the enzymatic determination of blood glucose,” Scandinavian Journal of Clinical and Laboratory Investigation, vol. 12, no. 4, pp. 402–407, 1960. 
+\bibitem{b7} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
+\bibitem{b8} B. E. Raabo and T. C. Terkildsen, “On the enzymatic determination of blood glucose,” Scandinavian Journal of Clinical and Laboratory Investigation, vol. 12, no. 4, pp. 402–407, 1960. 
 \end{thebibliography}

### 2022-12-12 paper-kelompok/main.tex

@@
 An interface which consists of an LCD and a set of buttons allows users to gather and view measurement results in a continous manner.
-The device had a dimension of 120 x 131 x 207 mmˆ3 with the weight of 0.832 kg.
+The device had a dimension of 120 x 131 x 207 mm\textsuperscript{3} with the weight of 0.832 kg.
 The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
 The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
-The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
+The transmittance error was ±11.22\% with ±9.88 nm wavelength error.
 The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
@@
     \item The measurement results can be displayed on an LCD and stored 
-    \item Portable (should be smaller than 420 x 300 x 180 mmˆ3 and weighs less than 2 kg)
+    \item Portable (should be smaller than 420 x 300 x 180 mm\textsuperscript{3} and weighs less than 2 kg)
 \end{itemize}
@@
 The yellow dye was evaluated at its peak absorbance wavelength of 427 nm.
-The pixel spectrum response in 400 nm is 45\% the spectrum response in 550 nm.
-Moreover, the lamp emission in 400 nm is 50\% the lamp emission in 700 nm.
-These effeciency drops caused low intensity readouts for blank measurements, which increased resolution and noise in lower wavelengths.
+The pixel spectrum response in 400 nm is 45\% the response in 550 nm.
+Moreover, the lamp emission in 400 nm is 50\% the emission in 700 nm.
+These effeciency drops caused low intensity readouts, which increased resolution and noise in lower wavelengths (400 to 450 nm).
 Increasing the lamp power was not an option because the heat would damage the plastic structures of the light path.
@@
 The first factor is the consistency of the internal structure of the product.
-During the implementation and testing process, it was shown that for each adjustment done for troubleshooting causes a shift in the component. 
-Light pathway obscured by other components cause a reduction in the light intensity which passes through the sample.
+During the implementation and testing process, it was shown that checking or opening the casing for each for each adjustment done for troubleshooting causes a shift in the component. 
+Light pathway obscured by other components cause a reduction in the light intensity which pass through the sample.
 
-From several tests, the treatment of the indium-tin oxide (ITO) coated glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
+From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
 ITO glass should have a holder, for example, given a casing with a clamp. 
-This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b5}.
+This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.
 
@@
 \subsection{Weight and Size}
-Weight measurement is done by placing the device on a digital scale which shows the weight of 0.832 kilograms. 
-The final dimension of the spectrophotometer are 120 x 131 x 207 mmˆ3, as shown in Fig. \ref{device_dimensions}
+Weight measurement is done by placing the device on a digital scale which shows the weight is 0.832 kilograms. 
+The final dimension of the spectrophotometer are 120 x 131 x 207 mm\textsuperscript{3}, as shown in Fig. \ref{device_dimensions}
 Device's dimensions are affected by the number of components used in the system and the optical configuration used. 
 The sensor's location, diffraction grating, and light source mainly influence the device's height. 
-The battery has a size of 70 x 42 x 21 mmˆ3, which significantly affects the determination of the minimum area of the base.
+The battery has a size of 70 x 42 x 21 mm\textsuperscript{3}, which significantly affects the determination of the minimum area of the base.
 In addition, the button component with a diagonal position uses a large enough area but leaves some empty space.

### 2022-12-12 paper-kelompok/main.tex
fig resize

--- 2022-12-11 paper-kelompok/main.tex
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-spec.png}}
+    \centerline{\includegraphics[scale=0.5]{lcd-spec.png}}
     \caption{The display of the result (left) and spectrum (right) page of a spectrum-mode measurement}
@@
 The user should click the REGRESS button to calculate the concentration of the unknown sample and view the standard curve plot (Fig. \ref{lcd-conc}).
-Each curve can store up to 10 sets of concentration and absorbance values.
+There are six curve slots available and each curve can store up to 10 sets of concentration and absorbance values.
 
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
+    \centerline{\includegraphics[scale=0.5]{lcd-conc.png}}
     \caption{The display of the table (left) and plot (right) page of a quantization-mode curve}

### 2022-12-12 paper-kelompok/main.tex
repeatability gram fix

--- 2022-12-12 paper-kelompok/main.tex
@@
 
-The wavelength precision and transmittance of the device are affected by several factors. 
-The first factor is the consistency of the internal structure of the product.
-During the implementation and testing process, it was shown that checking or opening the casing for each for each adjustment done for troubleshooting causes a shift in the component. 
-Light pathway obscured by other components cause a reduction in the light intensity which pass through the sample.
+The wavelength precision and transmittance of the device were affected by several factors. 
+The first factor was the stability of the internal structure of the product.
+During the implementation and testing process, it was observed that opening and adjusting the device's case for troubleshooting caused positional shifts of the components. 
+Light pathway obscured by other components could cause light intensity reduction.
 
-From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
-ITO glass should have a holder, for example, given a casing with a clamp. 
+From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produced a different level of precision. 
+ITO glass should have a holder, for example, a case with a clamp. 
 This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.
@@
     \begin{figure}[htbp]
-    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
+    \centerline{\includegraphics[scale=0.5]{lcd-conc.png}}
     \caption{The display of the table (left) and plot (right) page of a quantization-mode curve}

### 2022-12-12 paper-kelompok/main.tex
Minor grammatical revision

--- 2022-12-12 paper-kelompok/main.tex
@@
 \section{Introduction}
-The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluid.
-The number of people suffering from diabetes is rising, and there is over 1 in 10 adults are affected worldwide.
+The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluids.
+The number of people suffering from diabetes is rising, and over 1 in 10 adults in the world is affected.
 By 2045, 780 million people worldwide are predicted to live with diabetes\cite{b1}.

### 2022-12-12 paper-kelompok/main.tex
render rev3
tambah contoh includesvg

--- 2022-12-12 paper-kelompok/main.tex
@@
 \usepackage{xcolor}
+\usepackage{svg}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
+
+% folder figures sebagai root figure
+\graphicspath{{./figures/}}
 
@@
 \section{Introduction}
-The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluids.
-The number of people suffering from diabetes is rising, and over 1 in 10 adults in the world is affected.
-By 2045, 780 million people worldwide are predicted to live with diabetes\cite{b1}.
-Diabetes patients are at a higher risk of critical health problems than non-diabetic individuals.
-As a result, accurate monitoring of blood glucose concentrations in diabetic patients is crucial for real-time diabetes diagnosis.
-
-Currently, various methods detect and measure glucose concentrations.
+Currently, various methods detect and measure glucose concentrations in food matrices.
 These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic approaches, such as HPLC systems.
-While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b2}.
+While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
 However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
@@
 There are several enzymes that take glucose as a substrate and turn it into a product or byproduct that can be measured or detected.
-In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b2}.
+In particular, the development of spectrophotometric and colorimetric glucose assays has taken advantage of the activities of glucose oxidase and hexokinase enzyme\cite{b1}.
 Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide ($H_2O_2$).
-In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b3}.
+In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b2}.
 
-Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means\cite{b4,b5}.
+Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means\cite{b3,b4}.
 One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems.
-The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b4}.
+The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b3}.
 The DMF system mainly consists of a fluid layer located between the top and bottom plates.
-Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b6}.
+Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b5}.
 Droplet mixing allows chemical reactions to be done on chip.
@@
 The measurement readings will be sent to the control subsystem to be computed into absorbance values.
+
+%contoh gambar dengan svg
+
+\begin{figure}[htbp]
+    \centering
+    \includesvg[width=0.4\textwidth,inkscapelatex=false]{figures/test}
+    \caption{Test}
+    \label{Fig1}
+\end{figure}
 
@@
 Absorbance is directly proportional to the path length $l$ through the medium and the concentration $c$ of the absorbing substance for monochromatic radiation.
-Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b7}.
+Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b6}.
 
@@
 The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit. 
-The battery can be recharged with a 12 V adapter whenever the battery voltage is insufficient. 
+The battery can be recharged with a 12V adapter whenever the battery voltage is insufficient. 
 The power subsystem also provides information about the battery voltage value to be displayed to the user.
@@
 
-The power from the adapter is converted into 8.4 V (full capacity) using a charging module when charging is needed.
-The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4 V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6 V output to the microcontroller and other loads.
+The power from the adapter is converted into 8.4V (full capacity) using a charging module when charging is needed.
+The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6V output to the microcontroller and other loads.
 If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.
@@
 \subsection{Accuracy}
-Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b8}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
+Glucose samples were prepared using a glucose assay kit (Glucose (GO) Assay Kit, Sigma-Aldrich\cite{b7}) with concentration of 40 {\textmu}g/ml and 60 {\textmu}g/ml.
 The resulting liquid was then placed between two microscope slides spaced 0.5 mm apart to mimic the light path of the DMF cartridge.
@@
 \begin{thebibliography}{00}
-\bibitem{b1} “IDF Diabetes Atlas Tenth edition.” [Online]. Available: https://diabetesatlas.org/. [Accessed: 12-Dec-2022]. 
-\bibitem{b2} A. L. Galant, R. C. Kaufman, and J. D. Wilson, “Glucose: Detection and analysis,” Food Chemistry, vol. 188, pp. 149–160, 2015. 
-\bibitem{b3} H.
+\bibitem{b1} A. L. Galant, R. C. Kaufman, and J. D. Wilson, “Glucose: Detection and analysis,” Food Chemistry, vol. 188, pp. 149–160, 2015. 
+\bibitem{b2} H.
 V.
@@
 2020, doi: 10.1016/j.arabjc.2020.05.008.
-\bibitem{b4} Z.
+\bibitem{b3} Z.
 Gu, M.
@@
 11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
-\bibitem{b5} R.
+\bibitem{b4} R.
 B.
@@
 Weaver, “Integrated Chemical/biochemical sample collection, pre-concentration, and analysis on a digital microfluidic lab-on-a-chip platform,” SPIE Proceedings, 2004.
-\bibitem{b6} S.
+\bibitem{b5} S.
 Huang and R.
@@
 2019, doi: 10.1007/s42452-019-1693-8.
-\bibitem{b7} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
-\bibitem{b8} B. E. Raabo and T. C. Terkildsen, “On the enzymatic determination of blood glucose,” Scandinavian Journal of Clinical and Laboratory Investigation, vol. 12, no. 4, pp. 402–407, 1960. 
+\bibitem{b6} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
+\bibitem{b7} B. E. Raabo and T. C. Terkildsen, “On the enzymatic determination of blood glucose,” Scandinavian Journal of Clinical and Laboratory Investigation, vol. 12, no. 4, pp. 402–407, 1960. 
 \end{thebibliography}
